### 2014-03-04 manuscript.tex
Added files

\documentclass[a4paper, 12pt]{article}

\usepackage{natbib}
\usepackage{url}
\usepackage{graphicx}
\usepackage{fixltx2e,amsmath}
\usepackage{multirow}
\usepackage{natbib}

\def\bibfontsize{\small}
\def\authorfmt#1{\textsc{#1}}
\def\dcuand{\&}
\let\citeN=\citeasnoun

\MakeRobust{\eqref}

\bibliographystyle{apa}

\linespread{1.0}

\begin{document}

\begin{center}
  \textbf{\Large{Comparison of two opinion mining methods to classify opinions in online political discussions}}

\vspace{5mm}

\large{Hugo Hammer\footnote{hugo.hammer@hioa.no} \\
\vspace{1mm}
Department of Computer Science\\
Oslo and Akershus University College of Applied Sciences}

\vspace{5mm}

\large{Per-Erik Solberg \\
\vspace{1mm}
Spr\aa kbanken\\
The National Library of Norway}

\vspace{5mm}

\large{ Lilja \O vrelid\\
\vspace{1mm}
Department of Informatics\\
University of Oslo}

\end{center}

\begin{abstract}
Bla bla
\end{abstract}

keywords: \textit{}

\section{Introduction}
\label{sec:introduction}

Over the past years there has been an alarming growth in hate against minorities like Muslims, Jews, Gypsies and gays in Europe, driven by right wing populism parties and extremist organizations \citep{r4, r11}. A similar increase in hate speech has been observed on the Internet \citep{r6, s2}, and experts are concerned that individuals influenced by this web content may resort to violence as a result \citep{Strommen12, Sunde13}. Hateful speech is not only observed on extremst sites, but also as comments on Twitter, YouTube or online newspaper articles.

Social media and online discussions contain a wealth of information which can make us able to understand the extent of hate speech on the Internet. However, it turns out that academia is lacking research on social media and online radicalization \citep{s1}. Opinion mining is the discipline of automatically extracting opinions from a text material and may be one important tool in the understanding online radicalization. Opinion mining have mostly been analyzed toward extracting opinions in comments and reviews of commercial products, but have also been used to analyze political tweets and discussions, see e.g.  \citet{Tumasjan2010, Chen10}. Opinion mining towards political discussions is known to be hard since citations, irony and sarcasm is very common \citep{Bing12}.

Opinion classification is perhaps the most studied topic within opinion mining. It aims to classify a set of text as either positive or negative and sometimes also neutral. There are mainly two approaches, one based on machine learning and one based on based on using a list of known sentiments words (lexical approach). One simple lexical approach is to count the number of words with positive and negative sentiment in the document as suggested by \citet{Hu04}. One may classify the opinion of larger documents like movie or product reviews or smaller documents like tweets, comments or sentences. See \citet{Bing12}, chapters three to five and references therein for several methods to do opinion classification.

In this paper we focus on classifying the opinion of sentences and use the lexical-based approach. Suppose we want to classify the opinion toward a keyword, say 'immigration', in a sentence containing the keyword. One intuitive approach is to also find the the words with sentiment in the sentence and classify the sentiment of the sentence based on the polarity of these sentiment words. We expect that sentiment words that is close or related to the keyword in some sense is more important than other sentiment words in the sentence as suggested by \citet{Ding08}. An other approach is to use parsing to develop dependence paths between keywords and sentiment words, see e.g. \citet{Jiang11}. The aim of this paper is to compare the method suggested in \citet{Ding08} with a suggested method based on dependence paths to classify opinions in political discussions.

The paper is organized as follows.

\section{Opinion mining methods}
\label{sec:om}

\subsection{Word distance method}
\label{sec:wd}

\subsection{Dependence paths method}
\label{sec:dp}

\subsection{Measuring differences in opinion mining methods}
\label{sec:diff}

\section{Results}
\label{sec:results}

\section{Closing remarks}
\label{sec:cr}

\bibliography{bibl}

\end{document}

### 2014-03-04 toupper.py

@@ -1,0 +1,63 @@
+# Metode for automatisk å legge inn {} rundt store bokstaver i tittel.
+
+import re
+from subprocess import call
+call(["cp", "bibl.bib", "bibllowcase.bib"])
+
+r = open('bibllowcase.bib', 'r')
+w = open('bibl.bib', 'w')
+
+def addpar(line):
+    line = line.replace('{', '')    
+    line = line.replace('}', '')    
+    line = line.replace('A', '{A}')
+    line = line.replace('B', '{B}')
+    line = line.replace('C', '{C}')
+    line = line.replace('D', '{D}')
+    line = line.replace('E', '{E}')
+    line = line.replace('F', '{F}')
+    line = line.replace('G', '{G}')
+    line = line.replace('H', '{H}')
+    line = line.replace('I', '{I}')
+    line = line.replace('J', '{J}')
+    line = line.replace('K', '{K}')
+    line = line.replace('L', '{L}')
+    line = line.replace('M', '{M}')
+    line = line.replace('N', '{N}')
+    line = line.replace('O', '{O}')
+    line = line.replace('P', '{P}')
+    line = line.replace('Q', '{Q}')
+    line = line.replace('R', '{R}')
+    line = line.replace('S', '{S}')
+    line = line.replace('T', '{T}')
+    line = line.replace('U', '{U}')
+    line = line.replace('V', '{V}')
+    line = line.replace('A', '{A}')
+    line = line.replace('W', '{W}')
+    line = line.replace('X', '{X}')
+    line = line.replace('Y', '{Y}')
+    line = line.replace('Z', '{Z}')
+    line = line.replace('{{', '{')
+    line = line.replace('}}', '}')
+    line = line.replace('{{', '{')
+    line = line.replace('}}', '}')
+    line = line.replace('}{', '')
+    line = line.replace('title = ', 'title = {')    
+    line = line.replace(',\n', '},\n')    
+    return line
+
+title = re.compile('title =')
+for line in r:
+    res = title.findall(line)
+    if (len(res) > 0.5):
+        line = addpar(line)
+        print(line)
+    w.write(line)
+
+r.close()
+w.close()
+call(["mv", "bibllowcase.bib", "old/"])
+
+
+
+

### 2014-03-05 manuscript.tex
Changed manuscript

@@
 
-\large{Hugo Hammer\footnote{hugo.hammer@hioa.no} \\
-\vspace{1mm}
-Department of Computer Science\\
-Oslo and Akershus University College of Applied Sciences}
-
-\vspace{5mm}
-
-\large{Per-Erik Solberg \\
-\vspace{1mm}
-Spr\aa kbanken\\
-The National Library of Norway}
-
-\vspace{5mm}
-
-\large{ Lilja \O vrelid\\
-\vspace{1mm}
-Department of Informatics\\
-University of Oslo}
-
 \end{center}
@@
 A similar increase in hate speech has been observed on the Internet \citep{r6, s2}, and experts are concerned that individuals influenced by this web content may resort to violence as a result \citep{Strommen12, Sunde13}.
-Hateful speech is not only observed on extremst sites, but also as comments on Twitter, YouTube or online newspaper articles.
+Hateful speech is not only observed on extremst sites, but also as comments on e.g.
+Twitter, YouTube and online newspaper articles.
 
@@
 Opinion mining is the discipline of automatically extracting opinions from a text material and may be one important tool in the understanding online radicalization.
-Opinion mining have mostly been analyzed toward extracting opinions in comments and reviews of commercial products, but have also been used to analyze political tweets and discussions, see e.g.
+Opinion mining has mostly been used to analyze opinions in comments and reviews about commercial products, but there are also examples of opinion mining towards political tweets and discussions, see e.g.
 \citet{Tumasjan2010, Chen10}.
@@
 It aims to classify a set of text as either positive or negative and sometimes also neutral.
-There are mainly two approaches, one based on machine learning and one based on based on using a list of known sentiments words (lexical approach).
+There are mainly two approaches, one based on machine learning and one based on based on using a list of words with given sentiment scores (lexical approach).
 One simple lexical approach is to count the number of words with positive and negative sentiment in the document as suggested by \citet{Hu04}.
 One may classify the opinion of larger documents like movie or product reviews or smaller documents like tweets, comments or sentences.
-See \citet{Bing12}, chapters three to five and references therein for several methods to do opinion classification.
+See \citet{Bing12}, chapters three to five and references therein for the description of several opinion classification methods.
 
-In this paper we focus on classifying the opinion of sentences and use the lexical-based approach.
+In this paper we focus on classifying the opinion of sentences from political discussion by using the lexical-based approach.
 Suppose we want to classify the opinion toward a keyword, say 'immigration', in a sentence containing the keyword.
 One intuitive approach is to also find the the words with sentiment in the sentence and classify the sentiment of the sentence based on the polarity of these sentiment words.
-We expect that sentiment words that is close or related to the keyword in some sense is more important than other sentiment words in the sentence as suggested by \citet{Ding08}.
-An other approach is to use parsing to develop dependence paths between keywords and sentiment words, see e.g.
+We expect that the importance of a keyword towards the keyword depends on the number of words between the sentiment and key word as suggested by \citet{Ding08}.
+An other approach is to use parsing to develop grammatical dependence paths between keywords and sentiment words, see e.g.
 \citet{Jiang11}.
-The aim of this paper is to compare the method suggested in \citet{Ding08} with a suggested method based on dependence paths to classify opinions in political discussions.
+The aim of this paper is to compare the performance of a word distance method \citep{Ding08} with a developed method based on grammatical dependence paths to classify opinions in political discussions.
 
@@
 
-\subsection{Measuring differences in opinion mining methods}
+\subsection{Measuring the performance of opinion mining methods}
 \label{sec:diff}

### 2014-03-14 manuscript.tex

@@
 
-In this paper we focus on classifying the opinion of sentences from political discussion by using the lexical-based approach.
-Suppose we want to classify the opinion toward a keyword, say 'immigration', in a sentence containing the keyword.
-One intuitive approach is to also find the the words with sentiment in the sentence and classify the sentiment of the sentence based on the polarity of these sentiment words.
-We expect that the importance of a keyword towards the keyword depends on the number of words between the sentiment and key word as suggested by \citet{Ding08}.
-An other approach is to use parsing to develop grammatical dependence paths between keywords and sentiment words, see e.g.
+In this paper we focus on classifying the opinion toward religious/political topics, say the Quran, in political discussion by using the lexical-based approach. 
+One intuitive approach is to find both the key word (e.g.
+Quran) and the words with sentiment in the sentence and classify the sentiment of the sentence based on the polarity of these sentiment words.
+We expect that statistically the importance of a sentiment word towards the keyword is related on the number of words between the sentiment and key word as suggested by \citet{Ding08}.
+Two other approaches is to automatically parse the material and either use the distance between key and sentiment word in the parse tree or develop grammatical dependence paths, see e.g.
 \citet{Jiang11}.
-The aim of this paper is to compare the performance of a word distance method \citep{Ding08} with a developed method based on grammatical dependence paths to classify opinions in political discussions.
+The aim of this paper is to compare the performance of a word distance method \citep{Ding08} with a developed method based on distance in parse tree and grammatical dependence paths to classify opinions in political discussions.
 
@@
 
+In this Section we present two methods to classify sentences to either positive, neutral or negative towards a keyword.
+Both methods follow the same general algorithm presented below which is inspired by  \citet{Ding08}.
+Both keywords, sentiment words and sentiment shifters can in general appear several times in a sentence.
+Sentiment shifters is words that potentially shift the sentiment of a sentence from positive to negative or negative to positive.
+E.g.
+``not happy'' have the opposite polarity than just ``happy''.
+We assume that we have a list of sentiment words each associated with a sentiment score representing the polarity and strength of the sentiment word.
+Let $kw_i, i \in \{1,2,\ldots,I\}$ represent appearance number $i$ of the keyword in the sentence.
+Further let $sw_{jk}, j \in \{1,2,\ldots,J\}, k \in\{1,2,\ldots,K_j\}$ be appearance number $k$ of sentiment word $j$.
+Thus, sentiment word $j$ appears a total of $K_j$ times in the sentence.
+Finally let $ss_{lm}, l \in \{1,2,\ldots,L\}, m \in\{1,2,\ldots,M_l\}$ be appearance number $m$ of sentiment shifter $l$.
+We compute a sentimen scoret, $S$, for the sentence as follows
+\begin{equation}
+  \label{eq:1}
+  S = \frac{1}{\ln{(IJK+1)}} \sum_{i=1}^{I} \sum_{j=1}^{J} \sum_{k=1}^{K} \text{Imp}(kw_i, sw_{jk})\cdot f(sw_{jk}, \mathbf{ss})
+\end{equation}
+where $\mathbf{ss}$ represents all the appearances of sentiment shifters in the sentence.
+The function Imp computes the importance of the sentiment word $sw_{jk}$ on the keyword appearance $kw_i$.
+This will be computed in different ways as described below.
+Further, the function $f$ computes whether the sentiment of $sw_{jk}$ should be shifted based on the sentiment shifters in the sentence.
+The function returns $-1$ (sentiment shift) if some of the sentiment shifters is within $d_{p}$ words in front or $d_{n}$ words behind $sw_{jk}$, respectively.
+Else $f$, returns $1$.
+We classify the opinion towards the keyword to be positive, neutral or negative if $S >= t_p$,  $t_p > S > t_n$ and  $S <= t_n$, respectively.
+The parameters $d_p, d_n, t_p$ and $t_n$ is tuned using a training set.
+
 \subsection{Word distance method}
@@
 
-\subsection{Dependence paths method}
+\subsection{Parse tree method}
 \label{sec:dp}

### 2014-03-18 manuscript.tex
Changed manuscript

@@
-\documentclass[a4paper, 12pt]{article}
+\documentclass[11pt]{article}
 
-\usepackage{natbib}
+\usepackage{acl2014}
+\usepackage{times}
 \usepackage{url}
+\usepackage{latexsym}
+
 \usepackage{graphicx}
@@
 \usepackage{multirow}
-\usepackage{natbib}
-
-\def\bibfontsize{\small}
-\def\authorfmt#1{\textsc{#1}}
-\def\dcuand{\&}
-\let\citeN=\citeasnoun
 
@@
 
-\bibliographystyle{apa}
+\bibliographystyle{acl}
 
@@
 \begin{center}
-  \textbf{\Large{Comparison of two opinion mining methods to classify opinions in online political discussions}}
+  \textbf{\Large{Classifying opinions in online political discussion -- comparison of two methods}}
 
@@
 
-Over the past years there has been an alarming growth in hate against minorities like Muslims, Jews, Gypsies and gays in Europe, driven by right wing populism parties and extremist organizations \citep{r4, r11}.
-A similar increase in hate speech has been observed on the Internet \citep{r6, s2}, and experts are concerned that individuals influenced by this web content may resort to violence as a result \citep{Strommen12, Sunde13}.
+Over the past years there has been an alarming growth in hate against minorities like Muslims, Jews, Gypsies and gays in Europe, driven by right wing populism parties and extremist organizations \cite{r4,r11}.
+A similar increase in hate speech has been observed on the Internet \cite{r6,s2}, and experts are concerned that individuals influenced by this web content may resort to violence as a result \cite{Strommen12,Sunde13}.
 Hateful speech is not only observed on extremst sites, but also as comments on e.g.
@@
 Social media and online discussions contain a wealth of information which can make us able to understand the extent of hate speech on the Internet.
-However, it turns out that academia is lacking research on social media and online radicalization \citep{s1}.
+However, it turns out that academia is lacking research on social media and online radicalization \cite{s1}.
 Opinion mining is the discipline of automatically extracting opinions from a text material and may be one important tool in the understanding online radicalization.
 Opinion mining has mostly been used to analyze opinions in comments and reviews about commercial products, but there are also examples of opinion mining towards political tweets and discussions, see e.g.
-\citet{Tumasjan2010, Chen10}.
-Opinion mining towards political discussions is known to be hard since citations, irony and sarcasm is very common \citep{Bing12}.
+Tumasjan et al.
+\shortcite{Tumasjan2010}; Chen et al.
+\shortcite{Chen10}.
+Opinion mining towards political discussions is known to be hard since citations, irony and sarcasm is very common \cite{Bing12}.
 
@@
 There are mainly two approaches, one based on machine learning and one based on based on using a list of words with given sentiment scores (lexical approach).
-One simple lexical approach is to count the number of words with positive and negative sentiment in the document as suggested by \citet{Hu04}.
+One simple lexical approach is to count the number of words with positive and negative sentiment in the document as suggested by Hu and Liu \shortcite{Hu04}.
 One may classify the opinion of larger documents like movie or product reviews or smaller documents like tweets, comments or sentences.
-See \citet{Bing12}, chapters three to five and references therein for the description of several opinion classification methods.
+See Liu \shortcite{Bing12}, chapters three to five and references therein for the description of several opinion classification methods.
 
 In this paper we focus on classifying the opinion toward religious/political topics, say the Quran, in political discussion by using the lexical-based approach. 
-One intuitive approach is to find both the key word (e.g.
+One intuitive approach is to find both the keyword (e.g.
 Quran) and the words with sentiment in the sentence and classify the sentiment of the sentence based on the polarity of these sentiment words.
-We expect that statistically the importance of a sentiment word towards the keyword is related on the number of words between the sentiment and key word as suggested by \citet{Ding08}.
+We expect that statistically the importance of a sentiment word towards the keyword is related on the number of words between the sentiment and key word as suggested by Ding et al.
+\shortcite{Ding08}.
 Two other approaches is to automatically parse the material and either use the distance between key and sentiment word in the parse tree or develop grammatical dependence paths, see e.g.
-\citet{Jiang11}.
-The aim of this paper is to compare the performance of a word distance method \citep{Ding08} with a developed method based on distance in parse tree and grammatical dependence paths to classify opinions in political discussions.
+Jiang et al.
+\shortcite{Jiang11}.
+The aim of this paper is to compare the performance of a word distance method \cite{Ding08} with a developed method based on distance in parse tree and grammatical dependence paths to classify opinions in political discussions.
 
@@
 In this Section we present two methods to classify sentences to either positive, neutral or negative towards a keyword.
-Both methods follow the same general algorithm presented below which is inspired by  \citet{Ding08}.
+Both methods follow the same general algorithm presented below which is inspired by Ding et al.
+\shortcite{Ding08} and is based on a sentiment lexicon.
 Both keywords, sentiment words and sentiment shifters can in general appear several times in a sentence.
@@
 Finally let $ss_{lm}, l \in \{1,2,\ldots,L\}, m \in\{1,2,\ldots,M_l\}$ be appearance number $m$ of sentiment shifter $l$.
-We compute a sentimen scoret, $S$, for the sentence as follows
+We
+compute a sentiment score, $S$, for the sentence as follows
 \begin{equation}
   \label{eq:1}
-  S = \frac{1}{\ln{(IJK+1)}} \sum_{i=1}^{I} \sum_{j=1}^{J} \sum_{k=1}^{K} \text{Imp}(kw_i, sw_{jk})\cdot f(sw_{jk}, \mathbf{ss})
+  S = \frac{1}{I}\sum_{i=1}^{I} \sum_{j=1}^{J} \sum_{k=1}^{K}\mathbf{imp}(kw_i, sw_{jk})\mathbf{s}(sw_{jk}, \mathbf{ss})    
 \end{equation}
-where $\mathbf{ss}$ represents all the appearances of sentiment shifters in the sentence.
-The function Imp computes the importance of the sentiment word $sw_{jk}$ on the keyword appearance $kw_i$.
+where the function Imp computes the importance of the sentiment word $sw_{jk}$ on the keyword appearance $kw_i$.
 This will be computed in different ways as described below.
-Further, the function $f$ computes whether the sentiment of $sw_{jk}$ should be shifted based on the sentiment shifters in the sentence.
-The function returns $-1$ (sentiment shift) if some of the sentiment shifters is within $d_{p}$ words in front or $d_{n}$ words behind $sw_{jk}$, respectively.
-Else $f$, returns $1$.
+Further, the function $\mathbf{s}$ computes whether the sentiment of $sw_{jk}$ should be shifted based on all the sentiment shifters in the sentence, denoted by $\mathbf{ss}$.
+The function $\mathbf{s}$ returns $-1$ (sentiment shift) if some of the sentiment shifters is within $d_{p}$ words in front or $d_{n}$ words behind $sw_{jk}$, respectively.
+Else $\mathbf{s}$, returns $1$.
 We classify the opinion towards the keyword to be positive, neutral or negative if $S >= t_p$,  $t_p > S > t_n$ and  $S <= t_n$, respectively.
@@
 
+For the word distance method we use the following Imp function
+\begin{equation}
+  \label{eq:2}
+  \mathbf{imp}(kw_i, sw_{jk}) = \frac{\mathbf{sentsc}(sw_{jk})}{\mathbf{worddist}(kw_i, sw_{jk})}
+\end{equation}
+where $\mathbf{sentsc}(sw_{jk})$ is the sentiment score of $sw_{jk}$ from the sentiment lexicon and $\mathbf{worddist}(kw_i, sw_{jk})$ is the number of words between $kw_i$ and $sw_{jk}$ in the sentence plus one.
+
 \subsection{Parse tree method}
@@
 
-\subsection{Measuring the performance of opinion mining methods}
-\label{sec:diff}
+LEGGE INN FRA LILJA OG PER ERIK OM PARSING OG DEPENDENCE PATHS.
 
-\section{Results}
+Let $\mathcal{D}$ denote the set of all important grammatical relations.
+The function $\mathbf{gram}(kw_i, sw_{jk})$ returns the grammatical relation, and if $\mathbf{gram}(kw_i, sw_{jk}) \in \mathcal{D}$, then the function $W_{\mathbf{dep}}(kw_i, sw_{jk}) \in [0,1]$, return the importance of the grammatical relation.
+Further let $\mathbf{treedist}(kw_i, sw_{jk})$ return the number of words between the two words in the parse tree plus one.
+The Imp function is computed as follows.
+If $\mathbf{gram}(kw_i, sw_{jk}) \in \mathcal{D}$ we set
+\begin{align}
+  \begin{split}
+  \mathbf{imp}&(kw_i, sw_{jk}) = \\
+  &\alpha \cdot \mathbf{sentsc}(sw_{jk}) W_{\mathbf{dep}}(kw_i, sw_{jk}) \\
+  +&(1 - \alpha) \cdot \dfrac{\mathbf{sentsc}(sw_{jk})}{\mathbf{treedist}(kw_i, sw_{jk})}    
+  \end{split}
+\end{align}
+where $\alpha \in [0,1]$ is parameter that weights the score from the important dependence path and the tree distance. If $\mathbf{gram}(kw_i, sw_{jk}) \not\in \mathcal{D}$ we simply set 
+\begin{align}
+  \begin{split}
+  \mathbf{imp}(kw_i, sw_{jk}) = \dfrac{\mathbf{sentsc}(sw_{jk})}{\mathbf{treedist}(kw_i, sw_{jk})}    
+  \end{split}
+\end{align}
+
+\section{Real data example}
 \label{sec:results}
+
+\subsection{Text material}
+
+We did not find any suitable annotated text material related to political discussions and therefore created our own.
+We manually selected 46 debate articles from the Norwegian online newspapers \textit{NRK Ytring, Dagbladet, Aftenposten, VG and Bergens Tidene}.
+To each debate article there were attached an discussion platform where readers could express their opinions and feelings towards the content of the debate article.
+All the text from the debate articles and the subsequent discussions were collected using text scraping \cite{Hammer13}.
+All the debate articles were related to religion and immigration and we wanted to classify the opinion towards the words with stem: \textit{islam, muslim, quran, allah, muhammed, imam and mosque}.
+This is typically topics that creates a lot of active discussions and disagreements.
+
+We automatically split the material into sentences and all sentences containing some of the keywords were selected for further analysis.
+If a sentence contained more than one keyword, e.g.
+both islam and muslim, the sentence were repeated one time for each key word.
+We could then measure the opinion towards each of the keywords in the sentence separately.
+
+Each sentence were manually annotated whether the commenter were positive, negative or neutral towards the key word in the sentence.
+Each sentence were evaluated individually.
+The sentences were annotated based on all our knowledge, e.g.
+a sentence like ``Muhammed is like Hitler'' would be annotated as a negative opinion towards Muhammed.
+Further, if a commenter presented a negative fact about the keyword, the sentence would be denoted as negative.\\
+INTERANNOTARY!!\\
+Finally the material were divided in to two parts where the first half of the debate articles with subsequent discussions where in the training set and the rest were the test set.
+The individuals working on finding the important dependence paths, did only use the training set and did never see the test set before the decisions about dependence paths were decided.
+
+\subsection{Sentiment lexicon}
+
+% Resultater
 

### 2014-03-18 about_NDT.tex
paragraph on the NDT.

\documentclass[a4paper, 12pt]{article}

\usepackage{natbib}
\usepackage{url}
\usepackage{graphicx}
\usepackage{fixltx2e,amsmath}
\usepackage{multirow}
\usepackage{natbib}

\def\bibfontsize{\small}
\def\authorfmt#1{\textsc{#1}}
\def\dcuand{\&}
\let\citeN=\citeasnoun

\MakeRobust{\eqref}

\bibliographystyle{apa}

\linespread{1.0}

\begin{document}
The parser used in this study is trained on the Norwegian Dependency Treebank (NDT). The NDT is a corpus built up at the National Library of Norway in the period 2011-2013, manually annotated with part-of-speech tags, morphological features, syntactic functions and dependency graphs \citep{Sol14, Sol13}. It consists of approximately 600 000 tokens, equally distributed between Norwegian Bokmål and Nynorsk, the two Norwegian written standards. Only the Bokmål subcorpus has been used here. A large proportion of the NDT is newspaper text, there are also parliament transcripts, government reports and texts with a more colloquial style from blogs.

\bibliography{bibl}

\end{document}

### 2014-03-18 manuscript.tex

@@
 ``not happy'' have the opposite polarity than just ``happy''.
-We assume that we have a list of sentiment words each associated with a sentiment score representing the polarity and strength of the sentiment word.
+We assume that we have a list of sentiment words each associated with a sentiment score representing the polarity and strength of the sentiment word (sentiment lexicon).
 Let $kw_i, i \in \{1,2,\ldots,I\}$ represent appearance number $i$ of the keyword in the sentence.
-Further let $sw_{jk}, j \in \{1,2,\ldots,J\}, k \in\{1,2,\ldots,K_j\}$ be appearance number $k$ of sentiment word $j$.
-Thus, sentiment word $j$ appears a total of $K_j$ times in the sentence.
-Finally let $ss_{lm}, l \in \{1,2,\ldots,L\}, m \in\{1,2,\ldots,M_l\}$ be appearance number $m$ of sentiment shifter $l$.
-We
-compute a sentiment score, $S$, for the sentence as follows
+Further let $sw_{j}, j \in \{1,2,\ldots,J\}$ be appearance number $j$ of a sentiment word in the sentence.
+Finally let $\textbf{ss} = (ss_1, ss_2, \ldots, ss_K)$ repressent the sentiment shifters in the sentence.
+We compute a sentiment score, $S$, for the sentence as follows
 \begin{equation}
   \label{eq:1}
-  S = \frac{1}{I}\sum_{i=1}^{I} \sum_{j=1}^{J} \sum_{k=1}^{K}\mathbf{imp}(kw_i, sw_{jk})\mathbf{s}(sw_{jk}, \mathbf{ss})    
+  S = \frac{1}{I}\sum_{i=1}^{I} \sum_{j=1}^{J} \mathbf{imp}(kw_i, sw_{j})\mathbf{shift}(sw_{j}, \mathbf{ss})    
 \end{equation}
-where the function Imp computes the importance of the sentiment word $sw_{jk}$ on the keyword appearance $kw_i$.
+where the function Imp computes the importance of the sentiment word $sw_{j}$ on the keyword appearance $kw_i$.
 This will be computed in different ways as described below.
-Further, the function $\mathbf{s}$ computes whether the sentiment of $sw_{jk}$ should be shifted based on all the sentiment shifters in the sentence, denoted by $\mathbf{ss}$.
-The function $\mathbf{s}$ returns $-1$ (sentiment shift) if some of the sentiment shifters is within $d_{p}$ words in front or $d_{n}$ words behind $sw_{jk}$, respectively.
-Else $\mathbf{s}$, returns $1$.
+Further, the function $\mathbf{shift}(sw_{j}, \mathbf{ss})$ computes whether the sentiment of $sw_{j}$ should be shifted based on all the sentiment shifters in the sentence.
+It returns $-1$ (sentiment shift) if some of the sentiment shifters is within $d_{p}$ words in front or $d_{n}$ words behind $sw_{j}$, respectively.
+Else the function, returns $1$ (no sentiment shift).
 We classify the opinion towards the keyword to be positive, neutral or negative if $S >= t_p$,  $t_p > S > t_n$ and  $S <= t_n$, respectively.
@@
   \label{eq:2}
-  \mathbf{imp}(kw_i, sw_{jk}) = \frac{\mathbf{sentsc}(sw_{jk})}{\mathbf{worddist}(kw_i, sw_{jk})}
+  \mathbf{imp}(kw_i, sw_{j}) = \frac{\mathbf{sentsc}(sw_{j})}{\mathbf{worddist}(kw_i, sw_{j})}
 \end{equation}
-where $\mathbf{sentsc}(sw_{jk})$ is the sentiment score of $sw_{jk}$ from the sentiment lexicon and $\mathbf{worddist}(kw_i, sw_{jk})$ is the number of words between $kw_i$ and $sw_{jk}$ in the sentence plus one.
+where $\mathbf{sentsc}(sw_{j})$ is the sentiment score of $sw_{j}$ from the sentiment lexicon and $\mathbf{worddist}(kw_i, sw_{j})$ is the number of words between $kw_i$ and $sw_{j}$ in the sentence plus one.
 
@@
 Let $\mathcal{D}$ denote the set of all important grammatical relations.
-The function $\mathbf{gram}(kw_i, sw_{jk})$ returns the grammatical relation, and if $\mathbf{gram}(kw_i, sw_{jk}) \in \mathcal{D}$, then the function $W_{\mathbf{dep}}(kw_i, sw_{jk}) \in [0,1]$, return the importance of the grammatical relation.
-Further let $\mathbf{treedist}(kw_i, sw_{jk})$ return the number of words between the two words in the parse tree plus one.
+The function $\mathbf{gram}(kw_i, sw_{j})$ returns the grammatical relation, and if $\mathbf{gram}(kw_i, sw_{j}) \in \mathcal{D}$, then the function $W_{\mathbf{dep}}(kw_i, sw_{j}) \in [0,1]$, return the importance of the grammatical relation.
+Further let $\mathbf{treedist}(kw_i, sw_{j})$ return the number of words between the two words in the parse tree plus one.
 The Imp function is computed as follows.
-If $\mathbf{gram}(kw_i, sw_{jk}) \in \mathcal{D}$ we set
+If $\mathbf{gram}(kw_i, sw_{j}) \in \mathcal{D}$ we use
 \begin{align}
   \begin{split}
-  \mathbf{imp}&(kw_i, sw_{jk}) = \\
-  &\alpha \cdot \mathbf{sentsc}(sw_{jk}) W_{\mathbf{dep}}(kw_i, sw_{jk}) \\
-  +&(1 - \alpha) \cdot \dfrac{\mathbf{sentsc}(sw_{jk})}{\mathbf{treedist}(kw_i, sw_{jk})}    
+    \label{eq:3}
+  \mathbf{imp}&(kw_i, sw_{j}) = \\
+  &\alpha \cdot \mathbf{sentsc}(sw_{j}) W_{\mathbf{dep}}(kw_i, sw_{j}) \\
+  +&(1 - \alpha) \cdot \dfrac{\mathbf{sentsc}(sw_{j})}{\mathbf{treedist}(kw_i, sw_{j})}    
   \end{split}
 \end{align}
-where $\alpha \in [0,1]$ is parameter that weights the score from the important dependence path and the tree distance. If $\mathbf{gram}(kw_i, sw_{jk}) \not\in \mathcal{D}$ we simply set 
-\begin{align}
-  \begin{split}
-  \mathbf{imp}(kw_i, sw_{jk}) = \dfrac{\mathbf{sentsc}(sw_{jk})}{\mathbf{treedist}(kw_i, sw_{jk})}    
-  \end{split}
-\end{align}
+where $\alpha \in [0,1]$ is parameter that weights the score from the important dependence path and the tree distance may be tuned from a training set.
+If $\mathbf{gram}(kw_i, sw_{j}) \not\in \mathcal{D}$ we simply use
+\begin{equation}
+  \label{eq:4}
+  \mathbf{imp}(kw_i, sw_{j}) = \dfrac{\mathbf{sentsc}(sw_{j})}{\mathbf{treedist}(kw_i, sw_{j})}    
+\end{equation}
+Note that when $\alpha = 0$, \eqref{eq:3} reduces to \eqref{eq:4}.
+
+\subsection{Statistical analysis of classification performance}
+
+We compare the classification performance of the methods above using random effect logistic regression.
+Let the stochastic variable $Y_{tm} \in \{0,1\}$ represents whether method $m \in 1,2,\ldots,M$ classified correct opinion to sentence number $t \in \{1,2,\ldots,T\}$, where $T$ is the number of sentences in the test set.
+We let $Y_{tm}, t = 1,2,\ldots,T, m = 1,2,\ldots,M$ being the 0-1 dependent variable of the regression model.
 
@@
 
-We automatically split the material into sentences and all sentences containing some of the keywords were selected for further analysis.
+We automatically divided the material into sentences and all sentences containing at least one keyword and one sentiment word were kept for further analysis.
 If a sentence contained more than one keyword, e.g.
-both islam and muslim, the sentence were repeated one time for each key word.
-We could then measure the opinion towards each of the keywords in the sentence separately.
+both islam and quran, the sentence were repeated one time for each keyword.
+We could then classify the opinion towards each of the keywords in the sentence consecutively.
 
-Each sentence were manually annotated whether the commenter were positive, negative or neutral towards the key word in the sentence.
+Each sentence were manually annotated whether the commenter were positive, negative or neutral towards the keyword in the sentence.
 Each sentence were evaluated individually.
@@
 INTERANNOTARY!!\\
-Finally the material were divided in to two parts where the first half of the debate articles with subsequent discussions where in the training set and the rest were the test set.
-The individuals working on finding the important dependence paths, did only use the training set and did never see the test set before the decisions about dependence paths were decided.
+Finally the material were divided in to two parts where the first half of the debate articles with subsequent discussions where in the training set and the rest were in the test set.
+The researcher working on finding the important dependence paths, did only use the training set and did never see the test set before the decisions about dependence paths were decided.
+After the division, the training and test set consisted of a total of 382 and 308 sentences, respectively.
+Table \ref{tab:1} summarizes the opinions in the sentences
+\begin{table}
+  \centering
+  \begin{tabular}{lcccc}
+             & Negative & Neutral & Positive \\\hline
+    Training & 174 (46\%) & 162 (42\%) & 46 (12\%)\\
+    Test     & 102 (33\%)& 182 (59\%) & 24 (8\%)
+  \end{tabular}
+  \caption{Manual annotation of training and test set.}
+  \label{tab:1}
+\end{table}
 
-\subsection{Sentiment lexicon}
+\subsection{Sentiment lexicon and sentiment shifters}
 
-% Resultater
+Unfortunately, no sentiment list exists for the Norwegian language and therefore we developed our own by manually translating the AFINN list \cite{Nielsen11}.
+We also manually added 1590 words relevant to political discussions  like 'deport', 'expel', 'extremist', 'terrorist' and so on, ending up with a list of 4067 Norwegian sentiment words.
+Each word were given a score from $-5$ to $5$ ranging from words with extremely negative sentiment (e.g.
+'behead') to highly positive sentiment words (e.g.
+'breathtaking').
+
+Several Norwegian sentiment shifters were considered but only the basic shifter 'not' improved the opinion classification and therefore only this word were used in the method.
+
+\subsection{classification performance}
+
+In this study we compared four different cases based on the general algorithm in \eqref{eq:1}.
+\begin{itemize}
+\item We use the \textbf{imp}-function presented in \eqref{eq:2}. We denote this case WD (word distance).
+\item For this case and the two below we use the \textbf{imp}-function in \eqref{eq:3}.
+Further we set $\alpha = 0$ meaning that we do not use the important dependence paths.
+We denote this case A0 ($\alpha = 0$).
+\item We set $\alpha = 1$ and for all dependency paths we set $W_{\mathbf{dep}} = 2/3$. We denote this case CW (constant weights).
+\item We set $\alpha = 1$ and for $W_{\mathbf{dep}}$ we use the weights presented in Table ??????. We denote this case OD (optimal use of dependence paths)
+\end{itemize}
+For each case we used the training set to manually tune the parameters $d_p, d_n, t_p$ and $t_n$ of the method. The parameters were tuned to optimize the number of correct classifications.
+
+Table \ref{tab:2} shows the optimal parameter values of $d_p, d_n, t_p$ and $t_n$ and the classification performance for different cases. 
+\begin{table}
+  \centering
+  \begin{tabular}{lcccccl}
+       & $d_p$ & $d_n$ & $t_p$ & $t_n$ & Correct   & p-val \\ \hline
+    WD &    2  &   0  & 0.7  &  0.0  & 142 (46\%) & \\
+    A0 &    2  &   0  & 2.5  &  0.3  & 161 (52\%) & 0.014 *\\
+    CW &    2  &   0  & 2.5  &  0.3  & 160 (52\%) & 0.020 *\\
+    OD &    2  &   0  & 2.5  &  0.3  & 162 (53\%) & 0.009 **
+  \end{tabular}
+  \caption{The second to the fifth column show the optimal values of the parameters of the model.
+The sixth column show the number of correct classifications and the last column shows the p-value that the method performs better than WD.
+Signif.
+codes: p-value $<$ 0.01:\,**, \, p-value $<$ 0.05:\,*.}
+  \label{tab:2}
+\end{table}
+We see that the sentiment shifter 'not' only have a positive effect on classification performance when it is in front of the sentiment word.
+We see that using dependence tree distances (case A0) the classification results is significantly improved compared word distance in the sentence (case WD) (p-value = 0.014).
+Also including the important dependence paths (case OD) further improves the classification performance, but the improvement is not significant compared to case A0.
 
@@
 
+In this paper we have analyzed if parsing can improve
+
 \bibliography{bibl}

### 2014-03-18 manuscript.tex
Changed manustript

@@
 \subsection{Statistical analysis of classification performance}
+\label{sec:sa}
 
-We compare the classification performance of the methods above using random effect logistic regression.
-Let the stochastic variable $Y_{tm} \in \{0,1\}$ represents whether method $m \in 1,2,\ldots,M$ classified correct opinion to sentence number $t \in \{1,2,\ldots,T\}$, where $T$ is the number of sentences in the test set.
-We let $Y_{tm}, t = 1,2,\ldots,T, m = 1,2,\ldots,M$ being the 0-1 dependent variable of the regression model.
+We compare the classification performance of a set of $M$ different methods, denoted as $\Pi_1, \Pi_2, \ldots, \Pi_M$, using a random effect logistic regression.
+Let the stochastic variable $Y_{tm} \in \{0,1\}$ represents whether method $\Pi_m, \, m \in \{1,2,\ldots,M\}$ classified the correct opinion to sentence number $t \in \{1,2,\ldots,T\}$, where $T$ is the number of sentences in the test set.
+We let $Y_{tm}$ being the dependent variable of the regression model.
+The different methods $\Pi_1, \Pi_2, \ldots, \Pi_M$ is included as a categorical independent variable.
+We also assume that classification performance of the different methods depends on the sentence to be classified, thus the sentence number therefore is included as a random effect.
+The model is then formulated as
+\begin{align}
+  \label{eq:5}
+  \begin{split}
+    P(Y_{tm} = 1) &= \text{logit}(\mu + \Pi_m + \epsilon_t + \epsilon_{tm}) \\
+    P(Y_{tm} = 0) &= 1 - P(Y_{tm} = 1)
+  \end{split}
+ \end{align}
+where $\epsilon_t$ is the sentence number random effect and $\epsilon_{tm}$ is additional random noise.
+Fitting the model to the observed classification performance of the different methods we are able to see if the probability of classifying correctly significantly vary between the methods.
+
+The statistical analysis is performed using the statistical program R \cite{R} and the R package \verb|lme4| \cite{lme4}.
 
@@
 We manually selected 46 debate articles from the Norwegian online newspapers \textit{NRK Ytring, Dagbladet, Aftenposten, VG and Bergens Tidene}.
-To each debate article there were attached an discussion platform where readers could express their opinions and feelings towards the content of the debate article.
+To each debate article there were attached an discussion thread where readers could express their opinions and feelings towards the content of the debate article.
 All the text from the debate articles and the subsequent discussions were collected using text scraping \cite{Hammer13}.
-All the debate articles were related to religion and immigration and we wanted to classify the opinion towards the words with stem: \textit{islam, muslim, quran, allah, muhammed, imam and mosque}.
-This is typically topics that creates a lot of active discussions and disagreements.
+The debate articles were related to religion and immigration and we wanted to classify the opinion towards all words with stem: \textit{islam, muslim, quran, allah, muhammed, imam and mosque}.
+These are topics that often creates a lot of active discussions and disagreements.
 
@@
 We could then classify the opinion towards each of the keywords in the sentence consecutively.
+To assure that we do not underestimate the uncertainty in the statistical analysis, we see each repetition of the sentence as the same sentence with respect to the sentence random effect in the regression model in Section \ref{sec:sa}
 
@@
 \begin{table}
+  \caption{Manual annotation of training and test set.}
   \centering
@@
   \end{tabular}
-  \caption{Manual annotation of training and test set.}
   \label{tab:1}
@@
 
-\subsection{classification performance}
+\subsection{Classification performance}
 
-In this study we compared four different cases based on the general algorithm in \eqref{eq:1}.
+In this study we compared four different methods based on the general algorithm in \eqref{eq:1}.
 \begin{itemize}
-\item We use the \textbf{imp}-function presented in \eqref{eq:2}. We denote this case WD (word distance).
-\item For this case and the two below we use the \textbf{imp}-function in \eqref{eq:3}.
+\item We use the \textbf{imp}-function presented in \eqref{eq:2}. We denote this method WD (word distance).
+\item For this method and the two below we use the \textbf{imp}-function in \eqref{eq:3}.
 Further we set $\alpha = 0$ meaning that we do not use the important dependence paths.
-We denote this case A0 ($\alpha = 0$).
-\item We set $\alpha = 1$ and for all dependency paths we set $W_{\mathbf{dep}} = 2/3$. We denote this case CW (constant weights).
-\item We set $\alpha = 1$ and for $W_{\mathbf{dep}}$ we use the weights presented in Table ??????. We denote this case OD (optimal use of dependence paths)
+We denote this method A0 ($\alpha = 0$).
+\item We set $\alpha = 1$ and for all dependency paths we set $W_{\mathbf{dep}} = 2/3$. We denote this method CW (constant weights).
+\item We set $\alpha = 1$ and for $W_{\mathbf{dep}}$ we use the weights presented in Table ??????. We denote this method OD (optimal use of dependence paths)
 \end{itemize}
-For each case we used the training set to manually tune the parameters $d_p, d_n, t_p$ and $t_n$ of the method. The parameters were tuned to optimize the number of correct classifications.
+For each method we used the training set to manually tune the parameters $d_p, d_n, t_p$ and $t_n$ of the method. The parameters were tuned to optimize the number of correct classifications.
 
-Table \ref{tab:2} shows the optimal parameter values of $d_p, d_n, t_p$ and $t_n$ and the classification performance for different cases. 
+Table \ref{tab:2} shows the optimal parameter values of $d_p, d_n, t_p$ and $t_n$ and the classification performance for different methods. 
 \begin{table}
+  \caption{The second to the fifth column show the optimal values of the parameters of the model.
+The sixth column show the number of correct classifications and the last column shows the p-value that the method performs better than WD.}
   \centering
@@
        & $d_p$ & $d_n$ & $t_p$ & $t_n$ & Correct   & p-val \\ \hline
-    WD &    2  &   0  & 0.7  &  0.0  & 142 (46\%) & \\
-    A0 &    2  &   0  & 2.5  &  0.3  & 161 (52\%) & 0.014 *\\
-    CW &    2  &   0  & 2.5  &  0.3  & 160 (52\%) & 0.020 *\\
-    OD &    2  &   0  & 2.5  &  0.3  & 162 (53\%) & 0.009 **
+    WD &    2  &   0  & 0.7  &  0.0  & 145 (47\%) & \\
+    A0 &    2  &   0  & 2.0  &  0.3  & 161 (52\%) & 0.047 *\\
+    CW &    2  &   0  & 2.0  &  0.3  & 161 (52\%) & 0.048 *\\
+    OD &    2  &   0  & 2.0  &  0.3  & 162 (53\%) & 0.031 *
   \end{tabular}
-  \caption{The second to the fifth column show the optimal values of the parameters of the model.
-The sixth column show the number of correct classifications and the last column shows the p-value that the method performs better than WD.
-Signif.
-codes: p-value $<$ 0.01:\,**, \, p-value $<$ 0.05:\,*.}
   \label{tab:2}
@@
 We see that the sentiment shifter 'not' only have a positive effect on classification performance when it is in front of the sentiment word.
-We see that using dependence tree distances (case A0) the classification results is significantly improved compared word distance in the sentence (case WD) (p-value = 0.014).
-Also including the important dependence paths (case OD) further improves the classification performance, but the improvement is not significant compared to case A0.
+We see that using dependence tree distances (method A0) the classification results is significantly improved compared to using word distances in the sentence (method WD) (p-value = 0.047).
+Also including the important dependence paths (method OD) further improves the classification performance (p-value = 0.031).
 
@@
 
-In this paper we have analyzed if parsing can improve
+Classifying opinions in political discussions is hard because of the frequent use of irony, sarcasm and citations.
+
+In this paper we have compared the use of word distance between keyword and sentiment word against metrics related to parsed sentence information.
 

### 2014-03-19 manuscript.tex
Changed manuscript

@@
 A similar increase in hate speech has been observed on the Internet \cite{r6,s2}, and experts are concerned that individuals influenced by this web content may resort to violence as a result \cite{Strommen12,Sunde13}.
-Hateful speech is not only observed on extremst sites, but also as comments on e.g.
+Hateful speech is not only observed on extremist sites, but also as comments on e.g.
 Twitter, YouTube and online newspaper articles.
@@
 Quran) and the words with sentiment in the sentence and classify the sentiment of the sentence based on the polarity of these sentiment words.
-We expect that statistically the importance of a sentiment word towards the keyword is related on the number of words between the sentiment and key word as suggested by Ding et al.
+We expect that statistically the importance of a sentiment word towards the keyword is related to the number of words between the sentiment and key word as suggested by Ding et al.
 \shortcite{Ding08}.
@@
 \shortcite{Jiang11}.
-The aim of this paper is to compare the performance of a word distance method \cite{Ding08} with a developed method based on distance in parse tree and grammatical dependence paths to classify opinions in political discussions.
+The aim of this paper is to compare the performance of a word distance method \cite{Ding08} with novel methods based on distance in parse tree and grammatical dependence paths to classify opinions in political discussions.
 
@@
 Both methods follow the same general algorithm presented below which is inspired by Ding et al.
-\shortcite{Ding08} and is based on a sentiment lexicon.
+\shortcite{Ding08} and is based on a list of sentiment words each associated with a sentiment score representing the polarity and strength of the sentiment word (sentiment lexicon).
 Both keywords, sentiment words and sentiment shifters can in general appear several times in a sentence.
@@
 ``not happy'' have the opposite polarity than just ``happy''.
-We assume that we have a list of sentiment words each associated with a sentiment score representing the polarity and strength of the sentiment word (sentiment lexicon).
 Let $kw_i, i \in \{1,2,\ldots,I\}$ represent appearance number $i$ of the keyword in the sentence.
@@
 \end{equation}
-where the function Imp computes the importance of the sentiment word $sw_{j}$ on the keyword appearance $kw_i$.
+where the function \textbf{imp} computes the importance of the sentiment word $sw_{j}$ on the keyword appearance $kw_i$.
 This will be computed in different ways as described below.
@@
 
-For the word distance method we use the following Imp function
+For the word distance method we use the following \textbf{imp} function
 \begin{equation}
@@
 Let $\mathcal{D}$ denote the set of all important grammatical relations.
-The function $\mathbf{gram}(kw_i, sw_{j})$ returns the grammatical relation, and if $\mathbf{gram}(kw_i, sw_{j}) \in \mathcal{D}$, then the function $W_{\mathbf{dep}}(kw_i, sw_{j}) \in [0,1]$, return the importance of the grammatical relation.
+The function $\mathbf{gram}(kw_i, sw_{j})$ returns the grammatical relation, and if $\mathbf{gram}(kw_i, sw_{j}) \in \mathcal{D}$, then the function $W_{\mathbf{dep}}(kw_i, sw_{j}) \in [0,1]$, returns the importance of the grammatical relation.
 Further let $\mathbf{treedist}(kw_i, sw_{j})$ return the number of words between the two words in the parse tree plus one.
-The Imp function is computed as follows.
+The \textbf{imp} function is computed as follows.
 If $\mathbf{gram}(kw_i, sw_{j}) \in \mathcal{D}$ we use
@@
 \end{align}
-where $\alpha \in [0,1]$ is parameter that weights the score from the important dependence path and the tree distance may be tuned from a training set.
+where $\alpha \in [0,1]$ is a parameter that weights the score from the important dependence path and the tree distance and can be tuned using a training set.
 If $\mathbf{gram}(kw_i, sw_{j}) \not\in \mathcal{D}$ we simply use
@@
 
-We compare the classification performance of a set of $M$ different methods, denoted as $\Pi_1, \Pi_2, \ldots, \Pi_M$, using a random effect logistic regression.
+We compare the classification performance of a set of $M$ different methods, denoted as $\Pi_1, \Pi_2, \ldots, \Pi_M$, using random effect logistic regression.
 Let the stochastic variable $Y_{tm} \in \{0,1\}$ represents whether method $\Pi_m, \, m \in \{1,2,\ldots,M\}$ classified the correct opinion to sentence number $t \in \{1,2,\ldots,T\}$, where $T$ is the number of sentences in the test set.
-We let $Y_{tm}$ being the dependent variable of the regression model.
-The different methods $\Pi_1, \Pi_2, \ldots, \Pi_M$ is included as a categorical independent variable.
-We also assume that classification performance of the different methods depends on the sentence to be classified, thus the sentence number therefore is included as a random effect.
-The model is then formulated as
+We let $Y_{tm}$ be the dependent variable of the regression model.
+The different methods $\Pi_1, \Pi_2, \ldots, \Pi_M$ is included as a categorical independent variable in the regression model.
+We also assume that classification performance of the different methods depends on the sentence to be classified, thus the sentence number is included as a random effect.
+The regression model is formulated as
 \begin{align}
@@
 We manually selected 46 debate articles from the Norwegian online newspapers \textit{NRK Ytring, Dagbladet, Aftenposten, VG and Bergens Tidene}.
-To each debate article there were attached an discussion thread where readers could express their opinions and feelings towards the content of the debate article.
+To each debate article there were attached a discussion thread where readers could express their opinions and feelings towards the content of the debate article.
 All the text from the debate articles and the subsequent discussions were collected using text scraping \cite{Hammer13}.
 The debate articles were related to religion and immigration and we wanted to classify the opinion towards all words with stem: \textit{islam, muslim, quran, allah, muhammed, imam and mosque}.
-These are topics that often creates a lot of active discussions and disagreements.
+These are topics that typically creates a lot of active discussions and disagreements.
 
@@
 If a sentence contained more than one keyword, e.g.
-both islam and quran, the sentence were repeated one time for each keyword.
+both Islam and Quran, the sentence were repeated one time for each keyword in the final text material.
 We could then classify the opinion towards each of the keywords in the sentence consecutively.
@@
 a sentence like ``Muhammed is like Hitler'' would be annotated as a negative opinion towards Muhammed.
-Further, if a commenter presented a negative fact about the keyword, the sentence would be denoted as negative.\\
-INTERANNOTARY!!\\
+Further, if a commenter presented a negative fact about the keyword, the sentence would be denoted as negative.
+
+A random sample of 65 sentences from the original text material were annotated by a second annotator.
+These sentences were not included in either the training or test set.
+For these sentences, the two annotators agreed on 58 of them, which is an 89\% agreement, with a 95\% confidence interval equal to (79\%, 95\%) assuming that each sentence is independent.
+Since the sentences is drawn randomly from the population of all sentences this is a fair assumption.
+
 Finally the material were divided in to two parts where the first half of the debate articles with subsequent discussions where in the training set and the rest were in the test set.
@@
 
-Unfortunately, no sentiment list exists for the Norwegian language and therefore we developed our own by manually translating the AFINN list \cite{Nielsen11}.
-We also manually added 1590 words relevant to political discussions  like 'deport', 'expel', 'extremist', 'terrorist' and so on, ending up with a list of 4067 Norwegian sentiment words.
+Unfortunately, no sentiment lexicon existed for the Norwegian language and therefore we developed our own by manually translating the AFINN list \cite{Nielsen11}.
+We also manually added 1590 words relevant to political discussions  like 'deport', 'expel', 'extremist' and 'terrorist', ending up with a list of 4067 Norwegian sentiment words.
 Each word were given a score from $-5$ to $5$ ranging from words with extremely negative sentiment (e.g.
@@
 \item For this method and the two below we use the \textbf{imp}-function in \eqref{eq:3}.
-Further we set $\alpha = 0$ meaning that we do not use the important dependence paths.
+Further we set $\alpha = 0$ which means that we do not use the important dependence paths.
 We denote this method A0 ($\alpha = 0$).
@@
 
-Table \ref{tab:2} shows the optimal parameter values of $d_p, d_n, t_p$ and $t_n$ and the classification performance for different methods. 
+Table \ref{tab:2} shows the optimal parameter values of $d_p, d_n, t_p$ and $t_n$ tuned using the training set, and classification performance for the different methods on the test set using the parameter values tuned from the training set.
+The p-values are computed using the regression model presented in Section \ref{sec:sa}.
 \begin{table}
-  \caption{The second to the fifth column show the optimal values of the parameters of the model.
-The sixth column show the number of correct classifications and the last column shows the p-value that the method performs better than WD.}
+  \caption{The second to the fifth column show the optimal values of the parameters of the model tuned using the training set.
+The sixth column show the number of correct classifications and the last column shows p-values testing whether the method performs better than WD.}
   \centering
@@
     WD &    2  &   0  & 0.7  &  0.0  & 145 (47\%) & \\
-    A0 &    2  &   0  & 2.0  &  0.3  & 161 (52\%) & 0.047 *\\
-    CW &    2  &   0  & 2.0  &  0.3  & 161 (52\%) & 0.048 *\\
-    OD &    2  &   0  & 2.0  &  0.3  & 162 (53\%) & 0.031 *
+    A0 &    2  &   0  & 2.0  &  0.3  & 161 (52\%) & 0.023\\
+    CW &    2  &   0  & 2.0  &  0.3  & 161 (52\%) & 0.024\\
+    OD &    2  &   0  & 2.0  &  0.3  & 162 (53\%) & 0.016
   \end{tabular}
@@
 \end{table}
-We see that the sentiment shifter 'not' only have a positive effect on classification performance when it is in front of the sentiment word.
-We see that using dependence tree distances (method A0) the classification results is significantly improved compared to using word distances in the sentence (method WD) (p-value = 0.047).
-Also including the important dependence paths (method OD) further improves the classification performance (p-value = 0.031).
+We see that the sentiment shifter 'not' only have a positive effect on the classification performance when it is in front of the sentiment word.
+We see that using dependence tree distances (method A0) the classification results is significantly improved compared to using word distances in the sentence (method WD) (p-value = 0.023).
+Also classification based on important dependence paths (method OD) performs significantly better than WD.
+We also see that OD performs better than A0 (162 correct compared to 161), but this improvement is not statistically significant.
 
@@
 Classifying opinions in political discussions is hard because of the frequent use of irony, sarcasm and citations.
+In this paper we have compared the use of word distance between keyword and sentiment word against metrics related to parsed sentence information.
+Our results show that using dependence tree distances or important dependence paths, improves the classification performance compared to using word distance.
 
-In this paper we have compared the use of word distance between keyword and sentiment word against metrics related to parsed sentence information.
+Manually selecting important dependence paths for the aim of opinion mining is a hard task.
+A natural further step of our analysis is to expand the training and test material and use machine learning to see if there exists dependence paths that improve results compared to using dependence tree distance.
 

### 2014-03-19 about_NDT.tex
PES, a few changes to text and bibliography

@@
-\documentclass[a4paper, 12pt]{article}
+%
+% File acl2014.tex
+%
+% Contact: koller@ling.uni-potsdam.de, yusuke@nii.ac.jp
+%%
+%% Based on the style files for ACL-2013, which were, in turn,
+%% Based on the style files for ACL-2012, which were, in turn,
+%% based on the style files for ACL-2011, which were, in turn, 
+%% based on the style files for ACL-2010, which were, in turn, 
+%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
+%% based on the style files for EACL-2009 and IJCNLP-2008...
 
-\usepackage{natbib}
+%% Based on the style files for EACL 2006 by 
+%%e.agirre@ehu.es or Sergi.Balari@uab.es
+%% and that of ACL 08 by Joakim Nivre and Noah Smith
+
+\documentclass[11pt]{article}
+\usepackage{acl2014}
+\usepackage{times}
 \usepackage{url}
-\usepackage{graphicx}
-\usepackage{fixltx2e,amsmath}
-\usepackage{multirow}
-\usepackage{natbib}
+\usepackage{latexsym}
 
-\def\bibfontsize{\small}
-\def\authorfmt#1{\textsc{#1}}
-\def\dcuand{\&}
-\let\citeN=\citeasnoun
+%\setlength\titlebox{5cm}
 
-\MakeRobust{\eqref}
-
-\bibliographystyle{apa}
-
-\linespread{1.0}
+% You can expand the titlebox if you need extra space
+% to show all the authors. Please do not make the titlebox
+% smaller than 5cm (the original size); we will check this
+% in the camera-ready version and ask you to change it back.
 
@@
 The parser used in this study is trained on the Norwegian Dependency Treebank (NDT).
-The NDT is a corpus built up at the National Library of Norway in the period 2011-2013, manually annotated with part-of-speech tags, morphological features, syntactic functions and dependency graphs \citep{Sol14, Sol13}.
+The NDT is a corpus built up at the National Library of Norway in the period 2011-2013, manually annotated with part-of-speech tags, morphological features, syntactic functions and dependency graphs \cite{Sol14, Sol13}.
 It consists of approximately 600 000 tokens, equally distributed between Norwegian Bokmål and Nynorsk, the two Norwegian written standards.
@@
 A large proportion of the NDT is newspaper text, there are also parliament transcripts, government reports and texts with a more colloquial style from blogs.
+Detailed annotation guidelines in English will be available in April 2014 \cite{Kinn2013}.
 

### 2014-03-19 grammatical_dep-paths.tex
PES, a few changes to text and bibliography

%
% File acl2014.tex
%
% Contact: koller@ling.uni-potsdam.de, yusuke@nii.ac.jp
%%
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

%\setlength\titlebox{5cm}

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\begin{document}
A second way of determining the importance of a sentiment word towards a keyword based on syntactically parsed texts, is to establish a list of grammatical dependency paths between words, and test whether such paths exist between the keywords and the sentiment words in the material under investigation \cite{Jiang11}. The assumption would be that, if there is a meaningful grammatical relation between a keyword and a sentiment word, it is likely that they are semantically related to each other. Furthermore, it is reasonable to expect than some paths are stronger indicators of the overall sentiment of the sentence than others. To test this method, we have made a list of 42 grammatical dependency patsh and given them a score between 1-3. The higher the score is, the better indicator of sentiment the path is assumed to be. In the following paragraphs, we will present our reasoning behind the choice of paths and the weight we have given them. Table <x> lists all phe paths. The paths are written as follows: postag-keyword:postag-sentiment word{\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn({\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn etc.). \emph{Up} and \emph{dn} show whether the preceding you move up or down in the dependency tree. So the relation between a noun keyword and a verb sentiment word where the noun is the subject of the verb, is represented as subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up. The relation between a keyword and a sentiment noun where the former is the subject and the latter is the direct object of the same verb, is subst:subst{\textunderscore}{\textunderscore}SUBST{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn. Below, we argue for our choices of grammatical dependency path and the score we have given them.

\bibliography{bibl}

\end{document}

### 2014-03-19 table_grammatical_paths.tex
I wanted to include this table, but it is probably hard to fit it in...

%
% File acl2014.tex
%
% Contact: koller@ling.uni-potsdam.de, yusuke@nii.ac.jp
%%
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{covington}

%\setlength\titlebox{5cm}

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\begin{document}

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|l|l|}
\hline \bf{Path} & \bf{Path group} & \bf{Score} \\ \hline
subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up & 3 & subj-pred \\
subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}INFV{\textunderscore}dn & 3 & subj-pred \\
subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}INFV{\textunderscore}dn{\textunderscore}{\textunderscore}INFV{\textunderscore}dn & 3 & subj-pred \\
subst:verb{\textunderscore}{\textunderscore}KOORD{\textunderscore}up{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up & 3 & subj-pred \\
subst:verb{\textunderscore}{\textunderscore}KOORD{\textunderscore}up{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}INFV{\textunderscore}dn & 3 & subj-pred \\
subst:adj{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn & 3 & subj-pred \\
subst:adj{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}INFV{\textunderscore}dn{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn & 3 & subj-pred \\
subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn & 3 & subj-pred \\
subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}INFV{\textunderscore}dn{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn & 3 & subj-pred \\
subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn & 3 & subj-within pred \\
subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}INFV{\textunderscore}dn{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn & 3 & subj-within pred \\
subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn{\textunderscore}{\textunderscore}KOORD{\textunderscore}dn & 3 & subj-within pred \\
subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn{\textunderscore}{\textunderscore}DET{\textunderscore}dn & 3 & subj-within pred \\
subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn{\textunderscore}{\textunderscore}DET{\textunderscore}dn & 3 & subj-within pred \\
subst:adj{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn{\textunderscore}{\textunderscore}ATR{\textunderscore}dn & 3 & subj-within pred \\
subst:adj{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn{\textunderscore}{\textunderscore}ATR{\textunderscore}dn & 3 & subj-within pred \\
subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}ADV{\textunderscore}dn{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}dn & 2 & subj-within pred \\
subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}INFV{\textunderscore}dn{\textunderscore}{\textunderscore}ADV{\textunderscore}dn{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}dn & 2 & subj-within pred \\
subst:adj{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}ADV{\textunderscore}dn & 2 & subj-within pred \\
subst:adj{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}INFV{\textunderscore}dn{\textunderscore}{\textunderscore}ADV{\textunderscore}dn & 2 & subj-within pred \\
subst:verb{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ATR{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}up & 1 & subj-within pred \\
subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}KOORD{\textunderscore}dn & 1 & subj-within pred \\
subst:verb{\textunderscore}{\textunderscore}DOBJ{\textunderscore}up & 1 & pred-internal \\
subst:verb{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ADV{\textunderscore}up & 1 & pred-internal \\
subst:subst{\textunderscore}{\textunderscore}DOBJ{\textunderscore}up{\textunderscore}{\textunderscore}ADV{\textunderscore}dn{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}dn & 1 & pred-internal \\
subst:adj{\textunderscore}{\textunderscore}DOBJ{\textunderscore}up{\textunderscore}{\textunderscore}ADV{\textunderscore}dn & 1 & pred-internal \\
subst:adj{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ADV{\textunderscore}up & 1 & pred-internal \\
subst:verb{\textunderscore}{\textunderscore}DET{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}up & 1 & pred-internal \\
subst:adj{\textunderscore}{\textunderscore}ATR{\textunderscore}dn & 2 & NP-internal \\
subst:subst{\textunderscore}{\textunderscore}ATR{\textunderscore}dn{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}dn & 2 & NP-internal \\
subst:subst{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ATR{\textunderscore}up & 2 & NP-internal \\
subst:adj{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ATR{\textunderscore}up & 2 & NP-internal \\
subst:verb{\textunderscore}{\textunderscore}ATR{\textunderscore}dn & 2 & NP-internal \\
subst:subst{\textunderscore}{\textunderscore}KOORD{\textunderscore}dn & 2 & NP-internal \\
subst:subst{\textunderscore}{\textunderscore}KOORD{\textunderscore}up & 2 & NP-internal \\
subst:subst{\textunderscore}{\textunderscore}DET{\textunderscore}dn & 2 & NP-internal \\
subst:subst{\textunderscore}{\textunderscore}DET{\textunderscore}up & 2 & NP-internal \\
subst:adj{\textunderscore}{\textunderscore}ATR{\textunderscore}dn{\textunderscore}{\textunderscore}ADV{\textunderscore}dn & 1 & NP-internal \\
subst:verb{\textunderscore}{\textunderscore}ATR{\textunderscore}dn{\textunderscore}{\textunderscore}KOORD{\textunderscore}dn & 1 & NP-internal \\
subst:adj{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ATR{\textunderscore}up{\textunderscore}{\textunderscore}ATR{\textunderscore}dn & 1 & NP-internal \\
subst:adj{\textunderscore}{\textunderscore}ATR{\textunderscore}dn{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}dn{\textunderscore}{\textunderscore}ATR{\textunderscore}dn & 1 & NP-internal \\
subst:subst{\textunderscore}{\textunderscore}KOORD{\textunderscore}up{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ATR{\textunderscore}up & 3 & NP-internal \\
\hline
\end{tabular}
\end{center}
\caption{\label{grampath} Grammatical dependency paths }
\end{table}

\end{document}

### 2014-03-19 grammatical_dep-paths.tex
changes to the grammatical dependency paths section

@@
 \usepackage{latexsym}
+\usepackage{covington}
 
@@
 \begin{document}
-A second way of determining the importance of a sentiment word towards a keyword based on syntactically parsed texts, is to establish a list of grammatical dependency paths between words, and test whether such paths exist between the keywords and the sentiment words in the material under investigation \cite{Jiang11}.
-The assumption would be that, if there is a meaningful grammatical relation between a keyword and a sentiment word, it is likely that they are semantically related to each other.
+A second way of determining the importance of a sentiment word towards a target based on syntactically parsed texts, is to establish a list of grammatical dependency paths between words, and test whether such paths exist between the target and the sentiment words in the material under investigation \cite{Jiang11}.
+The assumption would be that, if there is a meaningful grammatical relation between a target and a sentiment word, it is likely that they are semantically related to each other.
 Furthermore, it is reasonable to expect than some paths are stronger indicators of the overall sentiment of the sentence than others.
-To test this method, we have made a list of 42 grammatical dependency patsh and given them a score between 1-3.
+To test this method, we have made a list of 42 grammatical dependency paths and given them a score between 1-3.
 The higher the score is, the better indicator of sentiment the path is assumed to be.
 In the following paragraphs, we will present our reasoning behind the choice of paths and the weight we have given them.
-Table <x> lists all phe paths.
-The paths are written as follows: postag-keyword:postag-sentiment word{\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn({\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn etc.).
-\emph{Up} and \emph{dn} show whether the preceding you move up or down in the dependency tree.
-So the relation between a noun keyword and a verb sentiment word where the noun is the subject of the verb, is represented as subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up.
-The relation between a keyword and a sentiment noun where the former is the subject and the latter is the direct object of the same verb, is subst:subst{\textunderscore}{\textunderscore}SUBST{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn.
-Below, we argue for our choices of grammatical dependency path and the score we have given them.
+The paths are written as follows: postag-target:postag-sentiment word{\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn({\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn etc.).
+\emph{Up} and \emph{dn} show whether you move up or down in the dependency tree.
+So the relation between a noun target and a verb sentiment word where the noun is the subject of the verb, is represented as subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up.
+The relation between a target noun and a sentiment noun where the former is the subject and the latter is the direct object of the same verb, is subst:subst{\textunderscore}{\textunderscore}SUBST{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn.
+
+A first group consists of paths from subject targets to sentiment predicates.
+Such paths can e.g.
+go from a subject to a verbal predicate, subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up, as in (\ref{verbpred}), or from a subject to an adjectival or nominal predicate in the context of a copular verb, as in (\ref{adpred}), subst:adj{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn or subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn.
+
+\begin{examples}
+\item\label{verbpred}
+\gll Ja, n{\aa} \textbf{jubler(sent.w.)} vel \textbf{muslimene(target)}.
+yes now exult probably muslims+the
+\glt 'Yes, the muslims probably exult now.'
+\glend
+
+\item\label{adpred}
+\gll [...] for meg er \textbf{Muhammed(target)} like \textbf{levende(sent.w.)} som min far [...].
+{} for me is Muhammad as alive as my father {}
+\glt 'To me, Muhammad is as much alive as my dad is.'
+\glend
+
+\end{examples}
+
+We have chosen to give subject-predicate paths the highest possible score, 3.
+Firstly, the combination of a subject and a predicate will result in a proposition, a statement which is evaluated as true or false \cite{Heim98}.
+We expect that a proposition typically will represent the opinion of the speaker, although e.g.
+irony and certain kinds of embedding can shift the truth evaluation in some cases \cite{Hooper73}.
+Secondly, if the predicate represents an event brought about by an intentional agent, such as \emph{jubler}, 'exult', in (\ref{verbpred}), the subject will typically represent that agent.
+If the predicate has a positive or negative sentiment, we expect that this sentiment is directed towards this intentional agent.
+
+A second group we have considered, contains paths from subject targets to sentiment words embedded within the predicate.
+Examples of such paths are those from the subject to the nominal direct object of a verb, as in (\ref{subjobj}), subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn.
+Paths from subjects into different kinds of adverbials are also a part of this group.
+
+\begin{examples}
+\item\label{subjobj}
+\gll [...] ekstreme \textbf{muslimer(target)} beg{\aa}r \textbf{voldshandlinger(sent.w.)} [...].
+{} extreme muslims commit {violent acts} {}
+\glt 'Extreme muslims commit violent acts.'
+\glend
+\end{examples}
+
+We consider paths from subjects to objects good indicators of sentiment and therefore give them the highest score, 3.
+The reasoning is much the same as for subject predicate paths: The statement is a proposition and the subject will often be the agent of the event.
+Also, the object, being an obligatory argument of the verb, is presumably closely semantically connected to it.
+Paths from subjects to adverbials, on the other hand, get a lower score, 2.
+This is because our experience is that the parser performs less well on adverbials.
+Also, adverbials are not obligatory arguments, and we therefore expect more semantic variation than for objects.
+
+The paths in our third group go from targets to sentiment words within the predicate.
+These include paths from nominal direct object target to verbal predicates, as in (\ref{objverb}), subst:verb{\textunderscore}{\textunderscore}DOBJ{\textunderscore}up, and from various kinds of adverbials to verbal predicates, among other things:
+
+\begin{examples}
+\item\label{objverb}
+\gll En Norsk dommer skal kontant \textbf{avvise(sent.w.)} \textbf{Sharia(target)} [...].
+a Norwegian judge shall strictly reject sharia {}
+\glt 'A Norwegian judge must strictly reject sharia.'
+\glend
+\end{examples}
+
+We assume that predicate-internal paths are less good indicators of sentiment than the above groups, as predicates need to combine with a subject to form a proposition.
+Also, arguments within the predicate usually do not represent the intentional agent of the event.
+Such paths will get the score 1.
+
+Our fourth and final group of dependency paths contains paths internal to the nominal phrase, such as from target nouns to attributive adjectives, as in (\ref{adjatr}), subst:adj{\textunderscore}{\textunderscore}ATR{\textunderscore}dn, and from target complements of attributive prepositions to target nouns, as in (\ref{substatr}), subst:subst{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ATR{\textunderscore}up:
+
+\begin{examples}
+\item\label{adjatr}
+\gll [...] \textbf{fundamentalistisk(sent.w.}) \textbf{islam(target)} [...]
+{} fundamentalist Islam {}
+\glt 'fundamentalist Islam'
+\glend
+
+\item\label{substatr}
+\gll [...] \textbf{kampen(sent.w} mot \textbf{islam(target)} [...]
+{} fight+the against Islam {}
+\glt 'the fight against Islam'
+\glend
+
+\end{examples}
+
+We suspect paths internal to the nominal phrase to be relatively good indicators of sentiment: A positively or negatively qualified noun will probably often represent the sentiment of the speaker.
+At the same time, a nominal phrase of this kind can be used in many different contexts where the holder of the sentiment is not the speaker, so we therefore expect such paths to be somewhat less good indicators than subject-predicate paths.
+We therefore assign them the score 2.
+
+Some complex paths receive a lower score than those indicated here, to compensate for parser inaccuracies.
 

### 2014-03-19 manuscript.tex
additions from PES to the text.

@@
 \usepackage{multirow}
+\usepackage{covington}
 
@@
 \label{sec:dp}
+LILJA: OM PARSING
 
-LEGGE INN FRA LILJA OG PER ERIK OM PARSING OG DEPENDENCE PATHS.
+The parser used in this study is trained on the Norwegian Dependency Treebank (NDT).
+The NDT is a corpus built up at the National Library of Norway in the period 2011-2013, manually annotated with part-of-speech tags, morphological features, syntactic functions and dependency graphs \cite{Sol14, Sol13}.
+It consists of approximately 600 000 tokens, equally distributed between Norwegian Bokmål and Nynorsk, the two Norwegian written standards.
+Only the Bokmål subcorpus has been used here.
+A large proportion of the NDT is newspaper text, there are also parliament transcripts, government reports and texts with a more colloquial style from blogs.
+Detailed annotation guidelines in English will be made available in April 2014 \cite{Kinn2013}.
+
+LILJA:OM DEPENDENCY DISTANCE?
+
+A second way of determining the importance of a sentiment word towards a target based on syntactically parsed texts, is to establish a list of grammatical dependency paths between words, and test whether such paths exist between the target and the sentiment words in the material under investigation \cite{Jiang11}.
+The assumption would be that, if there is a meaningful grammatical relation between a target and a sentiment word, it is likely that they are semantically related to each other.
+Furthermore, it is reasonable to expect than some paths are stronger indicators of the overall sentiment of the sentence than others.
+To test this method, we have made a list of 42 grammatical dependency paths and given them a score between 1-3.
+The higher the score is, the better indicator of sentiment the path is assumed to be.
+In the following paragraphs, we will present our reasoning behind the choice of paths and the weight we have given them.
+The paths are written as follows: postag-target:postag-sentiment word{\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn({\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn etc.).
+\emph{Up} and \emph{dn} show whether you move up or down in the dependency tree.
+So the relation between a noun target and a verb sentiment word where the noun is the subject of the verb, is represented as subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up.
+The relation between a target noun and a sentiment noun where the former is the subject and the latter is the direct object of the same verb, is subst:subst{\textunderscore}{\textunderscore}SUBST{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn.
+
+A first group consists of paths from subject targets to sentiment predicates.
+Such paths can e.g.
+go from a subject to a verbal predicate, subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up, as in (\ref{verbpred}), or from a subject to an adjectival or nominal predicate in the context of a copular verb, as in (\ref{adpred}), subst:adj{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn or subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn.
+
+\begin{examples}
+\item\label{verbpred}
+\gll Ja, n{\aa} \textbf{jubler(sent.w.)} vel \textbf{muslimene(target)}.
+yes now exult probably muslims+the
+\glt 'Yes, the muslims probably exult now.'
+\glend
+
+\item\label{adpred}
+\gll [...] for meg er \textbf{Muhammed(target)} like \textbf{levende(sent.w.)} som min far [...].
+{} for me is Muhammad as alive as my father {}
+\glt 'To me, Muhammad is as much alive as my dad is.'
+\glend
+
+\end{examples}
+
+We have chosen to give subject-predicate paths the highest possible score, 3.
+Firstly, the combination of a subject and a predicate will result in a proposition, a statement which is evaluated as true or false \cite{Heim98}.
+We expect that a proposition typically will represent the opinion of the speaker, although e.g.
+irony and certain kinds of embedding can shift the truth evaluation in some cases \cite{Hooper73}.
+Secondly, if the predicate represents an event brought about by an intentional agent, such as \emph{jubler}, 'exult', in (\ref{verbpred}), the subject will typically represent that agent.
+If the predicate has a positive or negative sentiment, we expect that this sentiment is directed towards this intentional agent.
+
+A second group we have considered, contains paths from subject targets to sentiment words embedded within the predicate.
+Examples of such paths are those from the subject to the nominal direct object of a verb, as in (\ref{subjobj}), subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn.
+Paths from subjects into different kinds of adverbials are also a part of this group.
+
+\begin{examples}
+\item\label{subjobj}
+\gll [...] ekstreme \textbf{muslimer(target)} beg{\aa}r \textbf{voldshandlinger(sent.w.)} [...].
+{} extreme muslims commit {violent acts} {}
+\glt 'Extreme muslims commit violent acts.'
+\glend
+\end{examples}
+
+We consider paths from subjects to objects good indicators of sentiment and therefore give them the highest score, 3.
+The reasoning is much the same as for subject predicate paths: The statement is a proposition and the subject will often be the agent of the event.
+Also, the object, being an obligatory argument of the verb, is presumably closely semantically connected to it.
+Paths from subjects to adverbials, on the other hand, get a lower score, 2.
+This is because our experience is that the parser performs less well on adverbials.
+Also, adverbials are not obligatory arguments, and we therefore expect more semantic variation than for objects.
+
+The paths in our third group go from targets to sentiment words within the predicate.
+These include paths from nominal direct object target to verbal predicates, as in (\ref{objverb}), subst:verb{\textunderscore}{\textunderscore}DOBJ{\textunderscore}up, and from various kinds of adverbials to verbal predicates, among other things:
+
+\begin{examples}
+\item\label{objverb}
+\gll En Norsk dommer skal kontant \textbf{avvise(sent.w.)} \textbf{Sharia(target)} [...].
+a Norwegian judge shall strictly reject sharia {}
+\glt 'A Norwegian judge must strictly reject sharia.'
+\glend
+\end{examples}
+
+We assume that predicate-internal paths are less good indicators of sentiment than the above groups, as predicates need to combine with a subject to form a proposition.
+Also, arguments within the predicate usually do not represent the intentional agent of the event.
+Such paths will get the score 1.
+
+Our fourth and final group of dependency paths contains paths internal to the nominal phrase, such as from target nouns to attributive adjectives, as in (\ref{adjatr}), subst:adj{\textunderscore}{\textunderscore}ATR{\textunderscore}dn, and from target complements of attributive prepositions to target nouns, as in (\ref{substatr}), subst:subst{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ATR{\textunderscore}up:
+
+\begin{examples}
+\item\label{adjatr}
+\gll [...] \textbf{fundamentalistisk(sent.w.}) \textbf{islam(target)} [...]
+{} fundamentalist Islam {}
+\glt 'fundamentalist Islam'
+\glend
+
+\item\label{substatr}
+\gll [...] \textbf{kampen(sent.w} mot \textbf{islam(target)} [...]
+{} fight+the against Islam {}
+\glt 'the fight against Islam'
+\glend
+
+\end{examples}
+
+We suspect paths internal to the nominal phrase to be relatively good indicators of sentiment: A positively or negatively qualified noun will probably often represent the sentiment of the speaker.
+At the same time, a nominal phrase of this kind can be used in many different contexts where the holder of the sentiment is not the speaker, so we therefore expect such paths to be somewhat less good indicators than subject-predicate paths.
+We therefore assign them the score 2.
+
+Some complex paths receive a lower score than those indicated here, to compensate for parser inaccuracies.
 

### 2014-03-20 manuscript.tex
Endring i introduksjon

@@
 
-In this paper we focus on classifying the opinion toward religious/political topics, say the Quran, in political discussion by using the lexical-based approach. 
+In this paper we focus on classifying the sentiment towards
+religious/political topics, say the Quran, in Norwegian political
+discussion. We use a lexicon-based approach where we classify the
+sentiment of a sentence based on the polarity of sentiment words in
+relation to a set of target words. We expect that statistically the
+importance of a sentiment word towards the keyword is related to the
+number of words between the sentiment and key word as suggested by
+Ding et al. \shortcite{Ding08}.  Information about the syntactic
+environment of certain words or phrases has in previous work also been
+shown to be useful for the task of sentiment classification
+\cite{Wil:Wie:Hof:09,Jiang11}. In this work we therefore compare the
+results obtained using a token-based distance measure with a novel
+syntax-based distance measure obtained using dependency graphs and
+further augmented with linguistically motivated syntactic patterns
+expressed as dependency paths.  We furthermore present a freely
+available corpus of Norwegian political discussion related to religion
+and immigration, which has been manually annotated for the sentiment
+expressed towards a set of target words, as well as a manually translated sentiment lexicon.
+
+%% In this paper we focus on classifying the opinion toward religious/political topics, say the Quran, in political discussion by using the lexical-based approach.
 One intuitive approach is to find both the keyword (e.g.
@@
 \label{sec:dp}
-LILJA: OM PARSING
+%LILJA: OM PARSING
+When determining the sentiment expressed towards a specific target word, the syntactic environment of this word and how it relates to sentiment-bearing words in the context may clearly be of importance.
 

### 2014-03-20 table_grammatical_paths.tex

@@
 subst:adj{\textunderscore}{\textunderscore}ATR{\textunderscore}dn{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}dn{\textunderscore}{\textunderscore}ATR{\textunderscore}dn & 1 & NP-internal \\
-subst:subst{\textunderscore}{\textunderscore}KOORD{\textunderscore}up{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ATR{\textunderscore}up & 3 & NP-internal \\
+subst:subst{\textunderscore}{\textunderscore}KOORD{\textunderscore}up{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ATR{\textunderscore}up & 1 & NP-internal \\
 \hline

### 2014-03-20 manuscript.tex
Described parsing, added new section in 3

@@
 
-The parser used in this study is trained on the Norwegian Dependency Treebank (NDT).
-The NDT is a corpus built up at the National Library of Norway in the period 2011-2013, manually annotated with part-of-speech tags, morphological features, syntactic functions and dependency graphs \cite{Sol14, Sol13}.
-It consists of approximately 600 000 tokens, equally distributed between Norwegian Bokmål and Nynorsk, the two Norwegian written standards.
-Only the Bokmål subcorpus has been used here.
-A large proportion of the NDT is newspaper text, there are also parliament transcripts, government reports and texts with a more colloquial style from blogs.
-Detailed annotation guidelines in English will be made available in April 2014 \cite{Kinn2013}.
+\paragraph{Dependency distance}
+One way of expressing the syntactic environment of a target word with respect to a sentiment word is to determine its distance in the dependency graph.
+We define a distance function $\mathbf{depdist}(kw_i, sw_{j})$ which returns the number of nodes between the two words in the parse tree plus one.
 
@@
 
+\subsection{Corpus postprocessing}
+The sentiment corpus was PoS-tagged and parsed using the
+Bohnet\&Nivre-parser \cite{Boh:Niv:12}. This parser is a
+transition-based dependency parser with joint tagger that implements
+global learning and a beam search for non-projective labeled
+dependency parsing.  This latter parser has recently outperformed
+pipeline systems (such as the Malt and MST parsers) both in terms of
+tagging and parsing accuracy for typologically diverse languages such
+as Chinese, English, and German. It has been reported to obtain a
+labeled accuracy of 87.7 for Norwegian \cite{Sol14}.  The parser is
+trained on the Norwegian Dependency Treebank (NDT). The NDT is a
+treebank created at the National Library of Norway in the period
+2011-2013, manually annotated with part-of-speech tags, morphological
+features, syntactic functions and dependency graphs \cite{Sol14,
+  Sol13}. It consists of approximately 600 000 tokens, equally
+distributed between Norwegian Bokm{\aa}l and Nynorsk, the two Norwegian
+written standards. Only the Bokm{\aa}l subcorpus has been used here. A
+large proportion of the NDT is newspaper text, there are also
+parliament transcripts, government reports and texts with a more
+colloquial style from blogs. Detailed annotation guidelines in English
+will be made available in April 2014 \cite{Kinn2013}.
+
 \subsection{Sentiment lexicon and sentiment shifters}

### 2014-03-20 manuscript.tex
Described dependency distance, added paragraph headings to section 2.2

@@
 %LILJA: OM PARSING
-When determining the sentiment expressed towards a specific target word, the syntactic environment of this word and how it relates to sentiment-bearing words in the context may clearly be of importance.
+When determining the sentiment expressed towards a specific target
+word, the syntactic environment of this word and how it relates to
+sentiment-bearing words in the context may clearly be of importance.
+In the following we present a modification of the scoring function described above to also take into account the syntactic environment of the target words.
+The function is defined over dependency graphs, i.e.
+connected, acyclic graphs expressing bilexical relations.
 
-\paragraph{Dependency distance}
-One way of expressing the syntactic environment of a target word with respect to a sentiment word is to determine its distance in the dependency graph.
-We define a distance function $\mathbf{depdist}(kw_i, sw_{j})$ which returns the number of nodes between the two words in the parse tree plus one.
+\paragraph{Dependency distance} One way of expressing the syntactic environment of a target word with respect to a sentiment word is to determine its distance in the dependency graph.
+We therefore define a distance function $\mathbf{depdist}(kw_i, sw_{j})$ which returns the number of nodes in the shortest dependency path from the target word to the sentiment word in the dependency.
 
-LILJA:OM DEPENDENCY DISTANCE?
-
+\paragraph{Dependency paths}
 A second way of determining the importance of a sentiment word towards a target based on syntactically parsed texts, is to establish a list of grammatical dependency paths between words, and test whether such paths exist between the target and the sentiment words in the material under investigation \cite{Jiang11}.
@@
 
+\paragraph{Modified scoring function}
 Let $\mathcal{D}$ denote the set of all important grammatical relations.
 The function $\mathbf{gram}(kw_i, sw_{j})$ returns the grammatical relation, and if $\mathbf{gram}(kw_i, sw_{j}) \in \mathcal{D}$, then the function $W_{\mathbf{dep}}(kw_i, sw_{j}) \in [0,1]$, returns the importance of the grammatical relation.
-Further let $\mathbf{treedist}(kw_i, sw_{j})$ return the number of words between the two words in the parse tree plus one.
+Further let $\mathbf{depdist}(kw_i, sw_{j})$ return the dependency distance, as described above.
 The \textbf{imp} function is computed as follows.

### 2014-03-20 manuscript.tex
minor typos etc

@@
 However, it turns out that academia is lacking research on social media and online radicalization \cite{s1}.
-Opinion mining is the discipline of automatically extracting opinions from a text material and may be one important tool in the understanding online radicalization.
+Opinion mining is the discipline of automatically extracting opinions from a text material and may be one important tool in the understanding of online radicalization.
 Opinion mining has mostly been used to analyze opinions in comments and reviews about commercial products, but there are also examples of opinion mining towards political tweets and discussions, see e.g.
@@
 It aims to classify a set of text as either positive or negative and sometimes also neutral.
-There are mainly two approaches, one based on machine learning and one based on based on using a list of words with given sentiment scores (lexical approach).
-One simple lexical approach is to count the number of words with positive and negative sentiment in the document as suggested by Hu and Liu \shortcite{Hu04}.
+There are mainly two approaches, one based on machine learning and one based on based on using a list of words with given sentiment scores (lexicon-based approach).
+One simple lexicon-based approach is to count the number of words with positive and negative sentiment in the document as suggested by Hu and Liu \shortcite{Hu04}.
 One may classify the opinion of larger documents like movie or product reviews or smaller documents like tweets, comments or sentences.
-See Liu \shortcite{Bing12}, chapters three to five and references therein for the description of several opinion classification methods.
+%% See Liu \shortcite{Bing12}, chapters three to five and references therein for the description of several opinion classification methods.
 
@@
 
-In this Section we present two methods to classify sentences to either positive, neutral or negative towards a keyword.
+In this Section we present two methods to classify sentences as either positive, neutral or negative towards a keyword.
 Both methods follow the same general algorithm presented below which is inspired by Ding et al.
@@
 Both keywords, sentiment words and sentiment shifters can in general appear several times in a sentence.
-Sentiment shifters is words that potentially shift the sentiment of a sentence from positive to negative or negative to positive.
+Sentiment shifters are words that potentially shift the sentiment of a sentence from positive to negative or negative to positive.
 E.g.
@@
 \paragraph{Modified scoring function}
-Let $\mathcal{D}$ denote the set of all important grammatical relations.
-The function $\mathbf{gram}(kw_i, sw_{j})$ returns the grammatical relation, and if $\mathbf{gram}(kw_i, sw_{j}) \in \mathcal{D}$, then the function $W_{\mathbf{dep}}(kw_i, sw_{j}) \in [0,1]$, returns the importance of the grammatical relation.
+Let $\mathcal{D}$ denote the set of all important dependency paths.
+The function $\mathbf{gram}(kw_i, sw_{j})$ returns the dependency path, and if $\mathbf{gram}(kw_i, sw_{j}) \in \mathcal{D}$, then the function $W_{\mathbf{dep}}(kw_i, sw_{j}) \in [0,1]$, returns the importance of the path.
 Further let $\mathbf{depdist}(kw_i, sw_{j})$ return the dependency distance, as described above.
@@
 \end{align}
-where $\alpha \in [0,1]$ is a parameter that weights the score from the important dependence path and the tree distance and can be tuned using a training set.
+where $\alpha \in [0,1]$ is a parameter that weights the score from the important dependency path and the tree distance and can be tuned using a training set.
 If $\mathbf{gram}(kw_i, sw_{j}) \not\in \mathcal{D}$ we simply use
@@
 The debate articles were related to religion and immigration and we wanted to classify the opinion towards all words with stem: \textit{islam, muslim, quran, allah, muhammed, imam and mosque}.
-These are topics that typically creates a lot of active discussions and disagreements.
+These are topics that typically create a lot of active discussions and disagreements.
 
@@
 
-Each sentence were manually annotated whether the commenter were positive, negative or neutral towards the keyword in the sentence.
-Each sentence were evaluated individually.
-The sentences were annotated based on all our knowledge, e.g.
+Each sentence was manually annotated as to whether the commenter was positive, negative or neutral towards the keyword in the sentence.
+Each sentence was evaluated individually.
+The sentences were annotated based on real-world knowledge, e.g.
 a sentence like ``Muhammed is like Hitler'' would be annotated as a negative opinion towards Muhammed.
@@
 
-A random sample of 65 sentences from the original text material were annotated by a second annotator.
+In order to assess inter-annotator agreement, a random sample of 65 sentences from the original text material was annotated by a second annotator.
 These sentences were not included in either the training or test set.
-For these sentences, the two annotators agreed on 58 of them, which is an 89\% agreement, with a 95\% confidence interval equal to (79\%, 95\%) assuming that each sentence is independent.
-Since the sentences is drawn randomly from the population of all sentences this is a fair assumption.
+For these sentences, the two annotators agreed on 58, which is an 89\% agreement, with a 95\% confidence interval equal to (79\%, 95\%) assuming that each sentence is independent.
+Since the sentences are drawn randomly from the population of all sentences this is a fair assumption.
 
-Finally the material were divided in to two parts where the first half of the debate articles with subsequent discussions where in the training set and the rest were in the test set.
-The researcher working on finding the important dependence paths, did only use the training set and did never see the test set before the decisions about dependence paths were decided.
+Finally the material was divided into two parts where the first half of the debate articles with subsequent discussions make up the training set and the rest constitutes a held-out test set.
+In the development of the important dependency paths, only the training set was used.
 After the division, the training and test set consisted of a total of 382 and 308 sentences, respectively.
@@
 \item For this method and the two below we use the \textbf{imp}-function in \eqref{eq:3}.
-Further we set $\alpha = 0$ which means that we do not use the important dependence paths.
+Further we set $\alpha = 0$ which means that we do not use the important dependency paths.
 We denote this method A0 ($\alpha = 0$).
 \item We set $\alpha = 1$ and for all dependency paths we set $W_{\mathbf{dep}} = 2/3$. We denote this method CW (constant weights).
-\item We set $\alpha = 1$ and for $W_{\mathbf{dep}}$ we use the weights presented in Table ??????. We denote this method OD (optimal use of dependence paths)
+\item We set $\alpha = 1$ and for $W_{\mathbf{dep}}$ we use the weights presented in Table ??????. We denote this method OD (optimal use of dependency paths)
 \end{itemize}
@@
 We see that the sentiment shifter 'not' only have a positive effect on the classification performance when it is in front of the sentiment word.
-We see that using dependence tree distances (method A0) the classification results is significantly improved compared to using word distances in the sentence (method WD) (p-value = 0.023).
-Also classification based on important dependence paths (method OD) performs significantly better than WD.
+We see that using dependency distances (method A0) the classification results is significantly improved compared to using word distances in the sentence (method WD) (p-value = 0.023).
+Also classification based on important dependency paths (method OD) performs significantly better than WD.
 We also see that OD performs better than A0 (162 correct compared to 161), but this improvement is not statistically significant.
@@
 In this paper we have compared the use of word distance between keyword and sentiment word against metrics related to parsed sentence information.
-Our results show that using dependence tree distances or important dependence paths, improves the classification performance compared to using word distance.
+Our results show that using dependency tree distances or important dependency paths, improves the classification performance compared to using word distance.
 
-Manually selecting important dependence paths for the aim of opinion mining is a hard task.
-A natural further step of our analysis is to expand the training and test material and use machine learning to see if there exists dependence paths that improve results compared to using dependence tree distance.
+Manually selecting important dependency paths for the aim of opinion mining is a hard task.
+A natural further step of our analysis is to expand the training and test material and use machine learning to see if there exists dependency paths that improve results compared to using dependency distance.
 

### 2014-03-20 manuscript.tex
added ref to dijkstra
changed opinion mining to sentiment analysis in whole document

@@
 
+\title{Sentiment classification in online political discussion -- comparison of two methods}
+
+\author{First Author \\
+  Affiliation / Address line 1 \\
+  Affiliation / Address line 2 \\
+  Affiliation / Address line 3 \\
+  {\tt email@domain} \\\And
+  Second Author \\
+  Affiliation / Address line 1 \\
+  Affiliation / Address line 2 \\
+  Affiliation / Address line 3 \\
+  {\tt email@domain} \\}
+
+\date{}
+
 \begin{document}
 
-\begin{center}
-  \textbf{\Large{Classifying opinions in online political discussion -- comparison of two methods}}
+%% \begin{center}
+%%   \textbf{\Large{Classifying opinions in online political discussion -- comparison of two methods}}
 
-\vspace{5mm}
+%% \vspace{5mm}
 
-\end{center}
-
+%% \end{center}
+\maketitle
 \begin{abstract}
@@
 However, it turns out that academia is lacking research on social media and online radicalization \cite{s1}.
-Opinion mining is the discipline of automatically extracting opinions from a text material and may be one important tool in the understanding of online radicalization.
-Opinion mining has mostly been used to analyze opinions in comments and reviews about commercial products, but there are also examples of opinion mining towards political tweets and discussions, see e.g.
+Sentiment analysis (SA) is the discipline of automatically determining sentiment in text material and may be one important tool in the understanding of online radicalization.
+SA has mostly been used to analyze opinions in comments and reviews about commercial products, but there are also examples of SA towards political tweets and discussions, see e.g.
 Tumasjan et al.
@@
 \shortcite{Chen10}.
-Opinion mining towards political discussions is known to be hard since citations, irony and sarcasm is very common \cite{Bing12}.
+SA of political discussions is known to be a difficult task since citations, irony and sarcasm is very common \cite{Bing12}.
 
-Opinion classification is perhaps the most studied topic within opinion mining.
-It aims to classify a set of text as either positive or negative and sometimes also neutral.
+Sentiment classification aims to classify a document or sentence as either positive or negative and sometimes also neutral.
 There are mainly two approaches, one based on machine learning and one based on based on using a list of words with given sentiment scores (lexicon-based approach).
@@
 
-\section{Opinion mining methods}
+\section{Proposed SA methods}
 \label{sec:om}
@@
 Else the function, returns $1$ (no sentiment shift).
-We classify the opinion towards the keyword to be positive, neutral or negative if $S >= t_p$,  $t_p > S > t_n$ and  $S <= t_n$, respectively.
+We classify the sentiment towards the keyword to be positive, neutral or negative if $S >= t_p$,  $t_p > S > t_n$ and  $S <= t_n$, respectively.
 The parameters $d_p, d_n, t_p$ and $t_n$ is tuned using a training set.
@@
 We therefore define a distance function $\mathbf{depdist}(kw_i, sw_{j})$ which returns the number of nodes in the shortest dependency path from the target word to the sentiment word in the dependency.
+The shortest path is determined using Dijkstra's shortest path algorithm \cite{Dij:59}.
 
@@
 Firstly, the combination of a subject and a predicate will result in a proposition, a statement which is evaluated as true or false \cite{Heim98}.
-We expect that a proposition typically will represent the opinion of the speaker, although e.g.
+We expect that a proposition typically will represent the sentiment of the speaker, although e.g.
 irony and certain kinds of embedding can shift the truth evaluation in some cases \cite{Hooper73}.
@@
 We compare the classification performance of a set of $M$ different methods, denoted as $\Pi_1, \Pi_2, \ldots, \Pi_M$, using random effect logistic regression.
-Let the stochastic variable $Y_{tm} \in \{0,1\}$ represents whether method $\Pi_m, \, m \in \{1,2,\ldots,M\}$ classified the correct opinion to sentence number $t \in \{1,2,\ldots,T\}$, where $T$ is the number of sentences in the test set.
+Let the stochastic variable $Y_{tm} \in \{0,1\}$ represents whether method $\Pi_m, \, m \in \{1,2,\ldots,M\}$ classified the correct sentiment to sentence number $t \in \{1,2,\ldots,T\}$, where $T$ is the number of sentences in the test set.
 We let $Y_{tm}$ be the dependent variable of the regression model.
@@
 All the text from the debate articles and the subsequent discussions were collected using text scraping \cite{Hammer13}.
-The debate articles were related to religion and immigration and we wanted to classify the opinion towards all words with stem: \textit{islam, muslim, quran, allah, muhammed, imam and mosque}.
+The debate articles were related to religion and immigration and we wanted to classify the sentiment towards all words with stem: \textit{islam, muslim, quran, allah, muhammed, imam and mosque}.
 These are topics that typically create a lot of active discussions and disagreements.
@@
 both Islam and Quran, the sentence were repeated one time for each keyword in the final text material.
-We could then classify the opinion towards each of the keywords in the sentence consecutively.
+We could then classify the sentiment towards each of the keywords in the sentence consecutively.
 To assure that we do not underestimate the uncertainty in the statistical analysis, we see each repetition of the sentence as the same sentence with respect to the sentence random effect in the regression model in Section \ref{sec:sa}
@@
 The sentences were annotated based on real-world knowledge, e.g.
-a sentence like ``Muhammed is like Hitler'' would be annotated as a negative opinion towards Muhammed.
+a sentence like ``Muhammed is like Hitler'' would be annotated as a negative sentiment towards Muhammed.
 Further, if a commenter presented a negative fact about the keyword, the sentence would be denoted as negative.
@@
 After the division, the training and test set consisted of a total of 382 and 308 sentences, respectively.
-Table \ref{tab:1} summarizes the opinions in the sentences
+Table \ref{tab:1} summarizes the sentiments in the sentences.
 \begin{table}
@@
 
-Several Norwegian sentiment shifters were considered but only the basic shifter 'not' improved the opinion classification and therefore only this word were used in the method.
+Several Norwegian sentiment shifters were considered but only the basic shifter 'not' improved the sentiment classification and therefore only this word were used in the method.
 
@@
 
-Classifying opinions in political discussions is hard because of the frequent use of irony, sarcasm and citations.
+Classifying sentiment in political discussions is hard because of the frequent use of irony, sarcasm and citations.
 In this paper we have compared the use of word distance between keyword and sentiment word against metrics related to parsed sentence information.
@@
 
-Manually selecting important dependency paths for the aim of opinion mining is a hard task.
+Manually selecting important dependency paths for the aim of sentiment analysis is a hard task.
 A natural further step of our analysis is to expand the training and test material and use machine learning to see if there exists dependency paths that improve results compared to using dependency distance.

### 2014-03-20 manuscript.tex
Attempt at making my paragraphs shorter.

@@
 
-\title{Sentiment classification in online political discussion -- comparison of two methods}
+\title{Sentiment classification of online political discussion -- a comparison of two methods}
 
@@
 \paragraph{Dependency paths}
-A second way of determining the importance of a sentiment word towards a target based on syntactically parsed texts, is to establish a list of grammatical dependency paths between words, and test whether such paths exist between the target and the sentiment words in the material under investigation \cite{Jiang11}.
-The assumption would be that, if there is a meaningful grammatical relation between a target and a sentiment word, it is likely that they are semantically related to each other.
+A second way of determining the importance of a sentiment word towards a target based on syntactically parsed texts, is to establish a list of grammatical dependency paths between words, and test whether such paths exist between the targets and sentiment words \cite{Jiang11}.
+The assumption would be that two words most likely are semantically related to each other if there is a meaningful grammatical relation between them.
 Furthermore, it is reasonable to expect than some paths are stronger indicators of the overall sentiment of the sentence than others.
-To test this method, we have made a list of 42 grammatical dependency paths and given them a score between 1-3.
+To test this method, we have made a list of 42 grammatical dependency paths, devided into four groups, and gave them a score between 1-3.
 The higher the score is, the better indicator of sentiment the path is assumed to be.
-In the following paragraphs, we will present our reasoning behind the choice of paths and the weight we have given them.
+In the following paragraphs, we will briefly present the groups of paths and the maximum score we have assigned in each group.
 The paths are written as follows: postag-target:postag-sentiment word{\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn({\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn etc.).
 \emph{Up} and \emph{dn} show whether you move up or down in the dependency tree.
-So the relation between a noun target and a verb sentiment word where the noun is the subject of the verb, is represented as subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up.
-The relation between a target noun and a sentiment noun where the former is the subject and the latter is the direct object of the same verb, is subst:subst{\textunderscore}{\textunderscore}SUBST{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn.
 
@@
 Such paths can e.g.
-go from a subject to a verbal predicate, subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up, as in (\ref{verbpred}), or from a subject to an adjectival or nominal predicate in the context of a copular verb, as in (\ref{adpred}), subst:adj{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn or subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn.
-
-\begin{examples}
-\item\label{verbpred}
-\gll Ja, n{\aa} \textbf{jubler(sent.w.)} vel \textbf{muslimene(target)}.
-yes now exult probably muslims+the
-\glt 'Yes, the muslims probably exult now.'
-\glend
-
-\item\label{adpred}
-\gll [...] for meg er \textbf{Muhammed(target)} like \textbf{levende(sent.w.)} som min far [...].
-{} for me is Muhammad as alive as my father {}
-\glt 'To me, Muhammad is as much alive as my dad is.'
-\glend
-
-\end{examples}
-
-We have chosen to give subject-predicate paths the highest possible score, 3.
-Firstly, the combination of a subject and a predicate will result in a proposition, a statement which is evaluated as true or false \cite{Heim98}.
-We expect that a proposition typically will represent the sentiment of the speaker, although e.g.
-irony and certain kinds of embedding can shift the truth evaluation in some cases \cite{Hooper73}.
-Secondly, if the predicate represents an event brought about by an intentional agent, such as \emph{jubler}, 'exult', in (\ref{verbpred}), the subject will typically represent that agent.
+go from a subject to a verbal predicate, subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up, or from a subject to an adjectival or nominal predicate in the context of a copular verb, subst:adj/subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn.
+Paths in this group can get the maximum score, 3.
+The combination of a subject and a predicate will result in a proposition, and we expect propositions to represent the opinion of the speaker in many cases.
+Also, the subject will often refer to the intentional agent of an event.
 If the predicate has a positive or negative sentiment, we expect that this sentiment is directed towards this intentional agent.
 
-A second group we have considered, contains paths from subject targets to sentiment words embedded within the predicate.
-Examples of such paths are those from the subject to the nominal direct object of a verb, as in (\ref{subjobj}), subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn.
+A second group we have considered, contains paths from subject targets to sentiment words embedded within the predicate, such as from the subject to the nominal direct object of a verb, subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn.
 Paths from subjects into different kinds of adverbials are also a part of this group.
-
-\begin{examples}
-\item\label{subjobj}
-\gll [...] ekstreme \textbf{muslimer(target)} beg{\aa}r \textbf{voldshandlinger(sent.w.)} [...].
-{} extreme muslims commit {violent acts} {}
-\glt 'Extreme muslims commit violent acts.'
-\glend
-\end{examples}
-
-We consider paths from subjects to objects good indicators of sentiment and therefore give them the highest score, 3.
-The reasoning is much the same as for subject predicate paths: The statement is a proposition and the subject will often be the agent of the event.
-Also, the object, being an obligatory argument of the verb, is presumably closely semantically connected to it.
-Paths from subjects to adverbials, on the other hand, get a lower score, 2.
-This is because our experience is that the parser performs less well on adverbials.
-Also, adverbials are not obligatory arguments, and we therefore expect more semantic variation than for objects.
+We consider paths from subjects to objects good indicators of sentiment and give them the highest score, 3, based on the same arguments as for subject-predicate paths.
+Paths into averbials get lower values, as adverbials often are less semantically connected to the predicate than objects.
 
 The paths in our third group go from targets to sentiment words within the predicate.
-These include paths from nominal direct object target to verbal predicates, as in (\ref{objverb}), subst:verb{\textunderscore}{\textunderscore}DOBJ{\textunderscore}up, and from various kinds of adverbials to verbal predicates, among other things:
-
-\begin{examples}
-\item\label{objverb}
-\gll En Norsk dommer skal kontant \textbf{avvise(sent.w.)} \textbf{Sharia(target)} [...].
-a Norwegian judge shall strictly reject sharia {}
-\glt 'A Norwegian judge must strictly reject sharia.'
-\glend
-\end{examples}
-
-We assume that predicate-internal paths are less good indicators of sentiment than the above groups, as predicates need to combine with a subject to form a proposition.
-Also, arguments within the predicate usually do not represent the intentional agent of the event.
+These include paths from nominal direct object target to verbal predicates, subst:verb{\textunderscore}{\textunderscore}DOBJ{\textunderscore}up, and from various kinds of adverbials to verbal predicates, etc.
+We assume that predicate-internal paths are less good indicators of sentiment than the above groups, as such paths do not constitute a proposition.
+Also, arguments within the predicate usually do not represent intentional agents.
 Such paths will get the score 1.
 
-Our fourth and final group of dependency paths contains paths internal to the nominal phrase, such as from target nouns to attributive adjectives, as in (\ref{adjatr}), subst:adj{\textunderscore}{\textunderscore}ATR{\textunderscore}dn, and from target complements of attributive prepositions to target nouns, as in (\ref{substatr}), subst:subst{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ATR{\textunderscore}up:
+Our fourth and final group of dependency paths contains paths internal to the nominal phrase, such as from target nouns to attributive adjectives, subst:adj{\textunderscore}{\textunderscore}ATR{\textunderscore}dn, and from target complements of attributive prepositions to target nouns, subst:subst{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ATR{\textunderscore}up.
+A positively or negatively qualified noun will probably often represent the sentiment of the speaker.
+At the same time, a nominal phrase of this kind can be used in many different contexts where the holder of the sentiment is not the speaker.
+We assign 2 as the maximum score.
+Table \ref{deppath} summarizes the groups of dependency paths.
 
-\begin{examples}
-\item\label{adjatr}
-\gll [...] \textbf{fundamentalistisk(sent.w.}) \textbf{islam(target)} [...]
-{} fundamentalist Islam {}
-\glt 'fundamentalist Islam'
-\glend
-
-\item\label{substatr}
-\gll [...] \textbf{kampen(sent.w} mot \textbf{islam(target)} [...]
-{} fight+the against Islam {}
-\glt 'the fight against Islam'
-\glend
-
-\end{examples}
-
-We suspect paths internal to the nominal phrase to be relatively good indicators of sentiment: A positively or negatively qualified noun will probably often represent the sentiment of the speaker.
-At the same time, a nominal phrase of this kind can be used in many different contexts where the holder of the sentiment is not the speaker, so we therefore expect such paths to be somewhat less good indicators than subject-predicate paths.
-We therefore assign them the score 2.
-
-Some complex paths receive a lower score than those indicated here, to compensate for parser inaccuracies.
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{|l|l|l|}
+\hline \bf Path group & \bf Number & \bf Score range \\ \hline
+Subj. to pred. & 9 & 3 \\
+Subj. to pred.-internal & 13 & 3-1 \\
+Pred.-internal & 6 & 1 \\
+NP-internal & 14 & 2-1 \\
+\hline
+\end{tabular}
+\end{center}
+\caption{\label{deppath} Dependency paths}
+\end{table}
 
@@
 
-\section{Real data example}
+\section{Linguistic resources}
 \label{sec:results}
 
-\subsection{Text material}
+\subsection{Sentiment corpus}
 
@@
 \begin{table}
-  \caption{Manual annotation of training and test set.}
   \centering
@@
   \label{tab:1}
+  \caption{Manual annotation of training and test set.}
 \end{table}
@@
 
-\subsection{Classification performance}
+\section{Experiments}
 

### 2014-03-20 manuscript.tex
Corrected a typo.
keyword to target + minor changes

@@
 
-keywords: \textit{}
+%keywords: \textit{}
 
@@
 sentiment of a sentence based on the polarity of sentiment words in
-relation to a set of target words. We expect that statistically the
-importance of a sentiment word towards the keyword is related to the
-number of words between the sentiment and key word as suggested by
-Ding et al. \shortcite{Ding08}.  Information about the syntactic
-environment of certain words or phrases has in previous work also been
-shown to be useful for the task of sentiment classification
-\cite{Wil:Wie:Hof:09,Jiang11}. In this work we therefore compare the
-results obtained using a token-based distance measure with a novel
-syntax-based distance measure obtained using dependency graphs and
-further augmented with linguistically motivated syntactic patterns
-expressed as dependency paths.  We furthermore present a freely
+relation to a set of target words in the sentence. We expect that
+statistically the importance of a sentiment word towards the target
+word is related to the number of words between the sentiment and
+target word as suggested by Ding et al. \shortcite{Ding08}.
+Information about the syntactic environment of certain words or
+phrases has in previous work also been shown to be useful for the task
+of sentiment classification \cite{Wil:Wie:Hof:09,Jiang11}. In this
+work we therefore compare the results obtained using a token-based
+distance measure with a novel syntax-based distance measure obtained
+using dependency graphs and further augmented with linguistically
+motivated syntactic patterns expressed as dependency paths. In order
+to evaluate the proposed methods, we furthermore present a freely
 available corpus of Norwegian political discussion related to religion
 and immigration, which has been manually annotated for the sentiment
-expressed towards a set of target words, as well as a manually translated sentiment lexicon.
+expressed towards a set of target words, as well as a manually
+translated sentiment lexicon.
 
 %% In this paper we focus on classifying the opinion toward religious/political topics, say the Quran, in political discussion by using the lexical-based approach.
-One intuitive approach is to find both the keyword (e.g.
+One intuitive approach is to find both the target word (e.g.
 Quran) and the words with sentiment in the sentence and classify the sentiment of the sentence based on the polarity of these sentiment words.
-We expect that statistically the importance of a sentiment word towards the keyword is related to the number of words between the sentiment and key word as suggested by Ding et al.
+We expect that statistically the importance of a sentiment word towards the target word is related to the number of words between the sentiment and key word as suggested by Ding et al.
 \shortcite{Ding08}.
@@
 
-In this Section we present two methods to classify sentences as either positive, neutral or negative towards a keyword.
+In this section we present two methods to classify sentences as either positive, neutral or negative towards a target word.
 Both methods follow the same general algorithm presented below which is inspired by Ding et al.
 \shortcite{Ding08} and is based on a list of sentiment words each associated with a sentiment score representing the polarity and strength of the sentiment word (sentiment lexicon).
-Both keywords, sentiment words and sentiment shifters can in general appear several times in a sentence.
+Both target words, sentiment words and sentiment shifters can in general appear several times in a sentence.
 Sentiment shifters are words that potentially shift the sentiment of a sentence from positive to negative or negative to positive.
@@
 ``not happy'' have the opposite polarity than just ``happy''.
-Let $kw_i, i \in \{1,2,\ldots,I\}$ represent appearance number $i$ of the keyword in the sentence.
+Let $kw_i, i \in \{1,2,\ldots,I\}$ represent appearance number $i$ of the target word in the sentence.
 Further let $sw_{j}, j \in \{1,2,\ldots,J\}$ be appearance number $j$ of a sentiment word in the sentence.
@@
 \end{equation}
-where the function \textbf{imp} computes the importance of the sentiment word $sw_{j}$ on the keyword appearance $kw_i$.
+where the function \textbf{imp} computes the importance of the sentiment word $sw_{j}$ on the target word appearance $kw_i$.
 This will be computed in different ways as described below.
 Further, the function $\mathbf{shift}(sw_{j}, \mathbf{ss})$ computes whether the sentiment of $sw_{j}$ should be shifted based on all the sentiment shifters in the sentence.
-It returns $-1$ (sentiment shift) if some of the sentiment shifters is within $d_{p}$ words in front or $d_{n}$ words behind $sw_{j}$, respectively.
+It returns $-1$ (sentiment shift) if some of the sentiment shifters are within $d_{p}$ words in front or $d_{n}$ words behind $sw_{j}$, respectively.
 Else the function, returns $1$ (no sentiment shift).
-We classify the sentiment towards the keyword to be positive, neutral or negative if $S >= t_p$,  $t_p > S > t_n$ and  $S <= t_n$, respectively.
-The parameters $d_p, d_n, t_p$ and $t_n$ is tuned using a training set.
+We classify the sentiment towards the target word to be positive, neutral or negative if $S >= t_p$,  $t_p > S > t_n$ and  $S <= t_n$, respectively.
+The parameters $d_p, d_n, t_p$ and $t_n$ is tuned using a training set, as described in section \ref{sec:exp} below.
 
@@
 \paragraph{Dependency distance} One way of expressing the syntactic environment of a target word with respect to a sentiment word is to determine its distance in the dependency graph.
-We therefore define a distance function $\mathbf{depdist}(kw_i, sw_{j})$ which returns the number of nodes in the shortest dependency path from the target word to the sentiment word in the dependency.
+We therefore define a distance function $\mathbf{depdist}(kw_i, sw_{j})$ which returns the number of nodes in the shortest dependency path from the target word to the sentiment word in the dependency graph.
 The shortest path is determined using Dijkstra's shortest path algorithm \cite{Dij:59}.
@@
 Furthermore, it is reasonable to expect than some paths are stronger indicators of the overall sentiment of the sentence than others.
-To test this method, we have made a list of 42 grammatical dependency paths, devided into four groups, and gave them a score between 1-3.
+To test this method, we have manually created a list of 42 grammatical dependency paths, divided into four groups, and given them a score between 1-3.
 The higher the score is, the better indicator of sentiment the path is assumed to be.
 In the following paragraphs, we will briefly present the groups of paths and the maximum score we have assigned in each group.
-The paths are written as follows: postag-target:postag-sentiment word{\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn({\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn etc.).
-\emph{Up} and \emph{dn} show whether you move up or down in the dependency tree.
+The paths are represented in the following format: postag-target:postag-sentiment word{\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn({\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn etc.).
+\emph{Up} and \emph{dn} indicate the direction of the traversed arc in the graph.
 
@@
 Paths from subjects into different kinds of adverbials are also a part of this group.
-We consider paths from subjects to objects good indicators of sentiment and give them the highest score, 3, based on the same arguments as for subject-predicate paths.
-Paths into averbials get lower values, as adverbials often are less semantically connected to the predicate than objects.
+We consider paths from subjects to objects to be good indicators of sentiment and assign them the highest score, 3, based on the same arguments as for subject-predicate paths.
+Paths into adverbials get lower values, as adverbials often are less semantically connected to the predicate than objects.
 
@@
 \end{center}
-\caption{\label{deppath} Dependency paths}
+\caption{\label{deppath} Grouping of dependency paths with the number of paths and score range for each group.}
+\label{tab:paths}
 \end{table}
@@
   &\alpha \cdot \mathbf{sentsc}(sw_{j}) W_{\mathbf{dep}}(kw_i, sw_{j}) \\
-  +&(1 - \alpha) \cdot \dfrac{\mathbf{sentsc}(sw_{j})}{\mathbf{treedist}(kw_i, sw_{j})}    
+  +&(1 - \alpha) \cdot \dfrac{\mathbf{sentsc}(sw_{j})}{\mathbf{depdist}(kw_i, sw_{j})}    
   \end{split}
@@
   \label{eq:4}
-  \mathbf{imp}(kw_i, sw_{j}) = \dfrac{\mathbf{sentsc}(sw_{j})}{\mathbf{treedist}(kw_i, sw_{j})}    
+  \mathbf{imp}(kw_i, sw_{j}) = \dfrac{\mathbf{sentsc}(sw_{j})}{\mathbf{depdist}(kw_i, sw_{j})}    
 \end{equation}
@@
 
-We did not find any suitable annotated text material related to political discussions and therefore created our own.
+We did not find any suitable annotated text material related to political discussions in norwegian and therefore created our own.
 We manually selected 46 debate articles from the Norwegian online newspapers \textit{NRK Ytring, Dagbladet, Aftenposten, VG and Bergens Tidene}.
@@
 All the text from the debate articles and the subsequent discussions were collected using text scraping \cite{Hammer13}.
-The debate articles were related to religion and immigration and we wanted to classify the sentiment towards all words with stem: \textit{islam, muslim, quran, allah, muhammed, imam and mosque}.
+The debate articles were related to religion and immigration and we wanted to classify the sentiment towards all forms of the following target words: \textit{islam, muslim, quran, allah, muhammed, imam and mosque}.
 These are topics that typically create a lot of active discussions and disagreements.
 
-We automatically divided the material into sentences and all sentences containing at least one keyword and one sentiment word were kept for further analysis.
-If a sentence contained more than one keyword, e.g.
-both Islam and Quran, the sentence were repeated one time for each keyword in the final text material.
-We could then classify the sentiment towards each of the keywords in the sentence consecutively.
+We automatically divided the material into sentences and all sentences containing at least one target word and one sentiment word were kept for further analysis.
+If a sentence contained more than one target word, e.g.
+both Islam and Quran, the sentence was repeated one time for each target word in the final text material.
+We could then classify the sentiment towards each of the target words in the sentence consecutively.
 To assure that we do not underestimate the uncertainty in the statistical analysis, we see each repetition of the sentence as the same sentence with respect to the sentence random effect in the regression model in Section \ref{sec:sa}
 
-Each sentence was manually annotated as to whether the commenter was positive, negative or neutral towards the keyword in the sentence.
+Each sentence was manually annotated as to whether the commenter was positive, negative or neutral towards the target word in the sentence.
 Each sentence was evaluated individually.
@@
 a sentence like ``Muhammed is like Hitler'' would be annotated as a negative sentiment towards Muhammed.
-Further, if a commenter presented a negative fact about the keyword, the sentence would be denoted as negative.
+Further, if a commenter presented a negative fact about the target word, the sentence would be denoted as negative.
 
@@
 Finally the material was divided into two parts where the first half of the debate articles with subsequent discussions make up the training set and the rest constitutes a held-out test set.
-In the development of the important dependency paths, only the training set was used.
+In the manual development of the important dependency paths, only the training set was used.
 After the division, the training and test set consisted of a total of 382 and 308 sentences, respectively.
-Table \ref{tab:1} summarizes the sentiments in the sentences.
+Table \ref{tab:1} summarizes the annotation found in the corpus.
 \begin{table}
@@
 2011-2013, manually annotated with part-of-speech tags, morphological
-features, syntactic functions and dependency graphs \cite{Sol14,
- Sol13}. It consists of approximately 600 000 tokens, equally
+features, syntactic functions and dependency graphs \cite{Sol14,Sol13}. It consists of approximately 600 000 tokens, equally
 distributed between Norwegian Bokm{\aa}l and Nynorsk, the two Norwegian
@@
 
-Several Norwegian sentiment shifters were considered but only the basic shifter 'not' improved the sentiment classification and therefore only this word were used in the method.
+Several Norwegian sentiment shifters were considered but only the basic shifter 'not' improved the sentiment classification and therefore only this word was used in the method.
 
 \section{Experiments}
-
-In this study we compared four different methods based on the general algorithm in \eqref{eq:1}.
+\label{sec:exp}
+In this study we compare four different methods based on the general algorithm in \eqref{eq:1}.
 \begin{itemize}
@@
 \item We set $\alpha = 1$ and for all dependency paths we set $W_{\mathbf{dep}} = 2/3$. We denote this method CW (constant weights).
-\item We set $\alpha = 1$ and for $W_{\mathbf{dep}}$ we use the weights presented in Table ??????. We denote this method OD (optimal use of dependency paths)
+\item We set $\alpha = 1$ and for $W_{\mathbf{dep}}$ we use the weights presented in Table \ref{tab:paths}. We denote this method OD (optimal use of dependency paths)
 \end{itemize}
@@
 \begin{table}
-  \caption{The second to the fifth column show the optimal values of the parameters of the model tuned using the training set.
-The sixth column show the number of correct classifications and the last column shows p-values testing whether the method performs better than WD.}
   \centering
@@
   \end{tabular}
+  \caption{The second to the fifth column show the optimal values of the parameters of the model tuned using the training set.
+The sixth column show the number of correct classifications and the last column shows p-values testing whether the method performs better than WD.}
   \label{tab:2}
 \end{table}
-We see that the sentiment shifter 'not' only have a positive effect on the classification performance when it is in front of the sentiment word.
-We see that using dependency distances (method A0) the classification results is significantly improved compared to using word distances in the sentence (method WD) (p-value = 0.023).
+We see that the sentiment shifter 'not' only has a positive effect on the classification performance when it is in front of the sentiment word.
+We see that using dependency distances (method A0) the classification results are significantly improved compared to using word distances in the sentence (method WD) (p-value = 0.023).
 Also classification based on important dependency paths (method OD) performs significantly better than WD.
@@
 Classifying sentiment in political discussions is hard because of the frequent use of irony, sarcasm and citations.
-In this paper we have compared the use of word distance between keyword and sentiment word against metrics related to parsed sentence information.
+In this paper we have compared the use of word distance between target word and sentiment word against metrics incorporating syntactic information.
 Our results show that using dependency tree distances or important dependency paths, improves the classification performance compared to using word distance.

### 2014-03-21 manuscript.tex
Changed manuscript

@@
 
-\title{Sentiment classification of online political discussion -- a comparison of two methods}
+\title{Sentiment classification of online political discussions: a comparison of a word-based and dependency-based method}
 
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\}
+\author{Hugo Lewi Hammer \\
+  Oslo and Akershus \\ University College \\ Department of Computer Science \\
+  {\tt hugo.hammer@hioa.no} \\ \And
+  Per Erik Solberg \\
+   Spr\aa kbanken \\ The National Library \\ of Norway\\
+  {\tt Per.Solberg@nb.no}\\ \And
+  Lilja \O vrelid \\
+   Department of Informatics \\ University of Oslo\\
+  {\tt liljao@ifi.uio.no}}
 
@@
 \begin{abstract}
-Bla bla
+Online political discussions have received a lot of attention over the past years.
+In this paper we compare two sentiment lexicon approaches to classify the sentiment of sentences from political discussions.
+The first approach is based on applying the number of words between the target and the sentiment words to weight the sentence sentiment score.
+The second approach is based on using the shortest paths between target and sentiment words in a dependency graph and linguistically motivated syntactic patterns expressed as dependence paths.
+The methods is tested on a corpus of sentences from online Norwegian political discussions.
+The results show that the method based on dependency graph performs significantly better than the first approach.
 \end{abstract}
@@
 
-Over the past years there has been an alarming growth in hate against minorities like Muslims, Jews, Gypsies and gays in Europe, driven by right wing populism parties and extremist organizations \cite{r4,r11}.
+%Over the past years there has been an alarming growth in hate against minorities like Muslims, Jews, Gypsies and gays in Europe, driven by right wing populism parties and extremist organizations \cite{r4,r11}.
 A similar increase in hate speech has been observed on the Internet \cite{r6,s2}, and experts are concerned that individuals influenced by this web content may resort to violence as a result \cite{Strommen12,Sunde13}.
@@
 
-Social media and online discussions contain a wealth of information which can make us able to understand the extent of hate speech on the Internet.
+%Social media and online discussions contain a wealth of information which can make us able to understand the extent of hate speech on the Internet.
 However, it turns out that academia is lacking research on social media and online radicalization \cite{s1}.
-Sentiment analysis (SA) is the discipline of automatically determining sentiment in text material and may be one important tool in the understanding of online radicalization.
+
+%hate and racism against is observed against minorities like Muslims, Jews, Gypsies and gays .
+Social media and online discussions contain a wealth of information which can make us able to understand the diversity of political opinions on the Internet.
+However, it turns out that academia is lacking research on social media and online radicalization \cite{s1}.
+
+Over the past years online political discussions have received a lot of attention.
+E.g.
+the Obama 2012 election team initiated an extensive use of text analytics and machine learning techniques towards online material to guide advertising campaigns, identifying key voters, and improve fundraising \cite{Issenberg12}.
+There also has been a lot of concert about the alarming growth in hate and racism against minorities like Muslims, Jews and Gypsies in online discussions \cite{r6,s2}.
+Sentiment analysis (SA) is the discipline of automatically determining sentiment in text material and may be one important tool in understanding the diversity of opinions on the Internet.
 SA has mostly been used to analyze opinions in comments and reviews about commercial products, but there are also examples of SA towards political tweets and discussions, see e.g.
@@
 
-Sentiment classification aims to classify a document or sentence as either positive or negative and sometimes also neutral.
+%Sentiment classification aims to classify a document or sentence as either positive or negative and sometimes also neutral.
 There are mainly two approaches, one based on machine learning and one based on based on using a list of words with given sentiment scores (lexicon-based approach).
@@
 
-The paper is organized as follows.
+%The paper is organized as follows.
 
@@
 ``not happy'' have the opposite polarity than just ``happy''.
-Let $kw_i, i \in \{1,2,\ldots,I\}$ represent appearance number $i$ of the target word in the sentence.
+Let $tw_i, i \in \{1,2,\ldots,I\}$ represent appearance number $i$ of the target word in the sentence.
 Further let $sw_{j}, j \in \{1,2,\ldots,J\}$ be appearance number $j$ of a sentiment word in the sentence.
@@
   \label{eq:1}
-  S = \frac{1}{I}\sum_{i=1}^{I} \sum_{j=1}^{J} \mathbf{imp}(kw_i, sw_{j})\mathbf{shift}(sw_{j}, \mathbf{ss})    
+  S = \frac{1}{I}\sum_{i=1}^{I} \sum_{j=1}^{J} \mathbf{imp}(tw_i, sw_{j})\mathbf{shift}(sw_{j}, \mathbf{ss})    
 \end{equation}
-where the function \textbf{imp} computes the importance of the sentiment word $sw_{j}$ on the target word appearance $kw_i$.
+where the function \textbf{imp} computes the importance of the sentiment word $sw_{j}$ on the target word appearance $tw_i$.
 This will be computed in different ways as described below.
@@
   \label{eq:2}
-  \mathbf{imp}(kw_i, sw_{j}) = \frac{\mathbf{sentsc}(sw_{j})}{\mathbf{worddist}(kw_i, sw_{j})}
+  \mathbf{imp}(tw_i, sw_{j}) = \frac{\mathbf{sentsc}(sw_{j})}{\mathbf{worddist}(tw_i, sw_{j})}
 \end{equation}
-where $\mathbf{sentsc}(sw_{j})$ is the sentiment score of $sw_{j}$ from the sentiment lexicon and $\mathbf{worddist}(kw_i, sw_{j})$ is the number of words between $kw_i$ and $sw_{j}$ in the sentence plus one.
+where $\mathbf{sentsc}(sw_{j})$ is the sentiment score of $sw_{j}$ from the sentiment lexicon and $\mathbf{worddist}(tw_i, sw_{j})$ is the number of words between $tw_i$ and $sw_{j}$ in the sentence plus one.
 
@@
 \paragraph{Dependency distance} One way of expressing the syntactic environment of a target word with respect to a sentiment word is to determine its distance in the dependency graph.
-We therefore define a distance function $\mathbf{depdist}(kw_i, sw_{j})$ which returns the number of nodes in the shortest dependency path from the target word to the sentiment word in the dependency graph.
+We therefore define a distance function $\mathbf{depdist}(tw_i, sw_{j})$ which returns the number of nodes in the shortest dependency path from the target word to the sentiment word in the dependency graph.
 The shortest path is determined using Dijkstra's shortest path algorithm \cite{Dij:59}.
@@
 Furthermore, it is reasonable to expect than some paths are stronger indicators of the overall sentiment of the sentence than others.
-To test this method, we have manually created a list of 42 grammatical dependency paths, divided into four groups, and given them a score between 1-3.
+To test this method, we have manually created a list of 42 grammatical dependency paths, divided into four groups, and given them a score from $0-1$.
 The higher the score is, the better indicator of sentiment the path is assumed to be.
@@
 go from a subject to a verbal predicate, subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up, or from a subject to an adjectival or nominal predicate in the context of a copular verb, subst:adj/subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn.
-Paths in this group can get the maximum score, 3.
+Paths in this group can get the maximum score, 1.
 The combination of a subject and a predicate will result in a proposition, and we expect propositions to represent the opinion of the speaker in many cases.
@@
 Paths from subjects into different kinds of adverbials are also a part of this group.
-We consider paths from subjects to objects to be good indicators of sentiment and assign them the highest score, 3, based on the same arguments as for subject-predicate paths.
+We consider paths from subjects to objects to be good indicators of sentiment and assign them the highest score, 1, based on the same arguments as for subject-predicate paths.
 Paths into adverbials get lower values, as adverbials often are less semantically connected to the predicate than objects.
@@
 Also, arguments within the predicate usually do not represent intentional agents.
-Such paths will get the score 1.
+Such paths will get the score $1/3$.
 
@@
 At the same time, a nominal phrase of this kind can be used in many different contexts where the holder of the sentiment is not the speaker.
-We assign 2 as the maximum score.
+We assign $2/3$ as the maximum score.
 Table \ref{deppath} summarizes the groups of dependency paths.
-
 \begin{table}[h]
 \begin{center}
-\begin{tabular}{|l|l|l|}
+\begin{tabular}{|l|cc|}
 \hline \bf Path group & \bf Number & \bf Score range \\ \hline
-Subj. to pred. & 9 & 3 \\
-Subj. to pred.-internal & 13 & 3-1 \\
-Pred.-internal & 6 & 1 \\
-NP-internal & 14 & 2-1 \\
+Subj. to pred. & $9$ & $1$ \\
+Subj. to pred.-internal & $13$ & $1/3-1$ \\
+Pred.-internal & $6$ & $1/3$ \\
+NP-internal & $14$ & $1/3-2/3$ \\
 \hline
@@
 \paragraph{Modified scoring function}
-Let $\mathcal{D}$ denote the set of all important dependency paths.
-The function $\mathbf{gram}(kw_i, sw_{j})$ returns the dependency path, and if $\mathbf{gram}(kw_i, sw_{j}) \in \mathcal{D}$, then the function $W_{\mathbf{dep}}(kw_i, sw_{j}) \in [0,1]$, returns the importance of the path.
-Further let $\mathbf{depdist}(kw_i, sw_{j})$ return the dependency distance, as described above.
+Let $\mathcal{D}$ denote the set of all salient dependency paths.
+The function $\mathbf{gram}(tw_i, sw_{j})$ returns the dependency path, and if $\mathbf{gram}(tw_i, sw_{j}) \in \mathcal{D}$, then the function $W_{\mathbf{dep}}(tw_i, sw_{j}) \in [0,1]$, returns the importance of the path.
+Further let $\mathbf{depdist}(tw_i, sw_{j})$ return the dependency distance, as described above.
 The \textbf{imp} function is computed as follows.
-If $\mathbf{gram}(kw_i, sw_{j}) \in \mathcal{D}$ we use
+If $\mathbf{gram}(tw_i, sw_{j}) \in \mathcal{D}$ we use
 \begin{align}
@@
     \label{eq:3}
-  \mathbf{imp}&(kw_i, sw_{j}) = \\
-  &\alpha \cdot \mathbf{sentsc}(sw_{j}) W_{\mathbf{dep}}(kw_i, sw_{j}) \\
-  +&(1 - \alpha) \cdot \dfrac{\mathbf{sentsc}(sw_{j})}{\mathbf{depdist}(kw_i, sw_{j})}    
+  \mathbf{imp}&(tw_i, sw_{j}) = \\
+  &\alpha \cdot \mathbf{sentsc}(sw_{j}) W_{\mathbf{dep}}(tw_i, sw_{j}) \\
+  +&(1 - \alpha) \cdot \dfrac{\mathbf{sentsc}(sw_{j})}{\mathbf{depdist}(tw_i, sw_{j})}    
   \end{split}
 \end{align}
-where $\alpha \in [0,1]$ is a parameter that weights the score from the important dependency path and the tree distance and can be tuned using a training set.
-If $\mathbf{gram}(kw_i, sw_{j}) \not\in \mathcal{D}$ we simply use
+where $\alpha \in [0,1]$ is a parameter that weights the score from the salient dependency path and the tree distance and can be tuned using a training set.
+If $\mathbf{gram}(tw_i, sw_{j}) \not\in \mathcal{D}$ we simply use
 \begin{equation}
   \label{eq:4}
-  \mathbf{imp}(kw_i, sw_{j}) = \dfrac{\mathbf{sentsc}(sw_{j})}{\mathbf{depdist}(kw_i, sw_{j})}    
+  \mathbf{imp}(tw_i, sw_{j}) = \dfrac{\mathbf{sentsc}(sw_{j})}{\mathbf{depdist}(tw_i, sw_{j})}    
 \end{equation}
 Note that when $\alpha = 0$, \eqref{eq:3} reduces to \eqref{eq:4}.
-
-\subsection{Statistical analysis of classification performance}
-\label{sec:sa}
-
-We compare the classification performance of a set of $M$ different methods, denoted as $\Pi_1, \Pi_2, \ldots, \Pi_M$, using random effect logistic regression.
-Let the stochastic variable $Y_{tm} \in \{0,1\}$ represents whether method $\Pi_m, \, m \in \{1,2,\ldots,M\}$ classified the correct sentiment to sentence number $t \in \{1,2,\ldots,T\}$, where $T$ is the number of sentences in the test set.
-We let $Y_{tm}$ be the dependent variable of the regression model.
-The different methods $\Pi_1, \Pi_2, \ldots, \Pi_M$ is included as a categorical independent variable in the regression model.
-We also assume that classification performance of the different methods depends on the sentence to be classified, thus the sentence number is included as a random effect.
-The regression model is formulated as
-\begin{align}
-  \label{eq:5}
-  \begin{split}
-    P(Y_{tm} = 1) &= \text{logit}(\mu + \Pi_m + \epsilon_t + \epsilon_{tm}) \\
-    P(Y_{tm} = 0) &= 1 - P(Y_{tm} = 1)
-  \end{split}
- \end{align}
-where $\epsilon_t$ is the sentence number random effect and $\epsilon_{tm}$ is additional random noise.
-Fitting the model to the observed classification performance of the different methods we are able to see if the probability of classifying correctly significantly vary between the methods.
-
-The statistical analysis is performed using the statistical program R \cite{R} and the R package \verb|lme4| \cite{lme4}.
 
@@
 
-We did not find any suitable annotated text material related to political discussions in norwegian and therefore created our own.
+We did not find any suitable annotated text material related to political discussions in Norwegian and therefore created our own.
 We manually selected 46 debate articles from the Norwegian online newspapers \textit{NRK Ytring, Dagbladet, Aftenposten, VG and Bergens Tidene}.
@@
 Finally the material was divided into two parts where the first half of the debate articles with subsequent discussions make up the training set and the rest constitutes a held-out test set.
-In the manual development of the important dependency paths, only the training set was used.
+In the manual development of the salient dependency paths, only the training set was used.
 After the division, the training and test set consisted of a total of 382 and 308 sentences, respectively.
@@
   \centering
-  \begin{tabular}{lcccc}
-             & Negative & Neutral & Positive \\\hline
+  \begin{tabular}{|l|ccc|c} 
+     \hline        & \bf Negative & \bf Neutral & \bf Positive \\\hline
     Training & 174 (46\%) & 162 (42\%) & 46 (12\%)\\
-    Test     & 102 (33\%)& 182 (59\%) & 24 (8\%)
+    Test     & 102 (33\%)& 182 (59\%) & 24 (8\%)\\\hline
   \end{tabular}
@@
 \label{sec:exp}
+
 In this study we compare four different methods based on the general algorithm in \eqref{eq:1}.
@@
 \item For this method and the two below we use the \textbf{imp}-function in \eqref{eq:3}.
-Further we set $\alpha = 0$ which means that we do not use the important dependency paths.
+Further we set $\alpha = 0$ which means that we do not use the salient dependency paths.
 We denote this method A0 ($\alpha = 0$).
@@
 
+\subsection{Statistical analysis of classification performance}
+\label{sec:sa}
+
+We compare the classification performance of a set of $M$ different methods, denoted as $\Pi_1, \Pi_2, \ldots, \Pi_M$, using random effect logistic regression.
+Let the stochastic variable $Y_{tm} \in \{0,1\}$ represents whether method $\Pi_m, \, m \in \{1,2,\ldots,M\}$ classified the correct sentiment to sentence number $t \in \{1,2,\ldots,T\}$, where $T$ is the number of sentences in the test set.
+We let $Y_{tm}$ be the dependent variable of the regression model.
+The different methods $\Pi_1, \Pi_2, \ldots, \Pi_M$ is included as a categorical independent variable in the regression model.
+We also assume that classification performance of the different methods depends on the sentence to be classified, thus the sentence number is included as a random effect.
+%The regression model is formulated as
+%\begin{align}
+%  \label{eq:5}
+%  \begin{split}
+%    P(Y_{tm} = 1) &= \text{logit}(\mu + \Pi_m + \epsilon_t + \epsilon_{tm}) \\
+%    P(Y_{tm} = 0) &= 1 - P(Y_{tm} = 1)
+%  \end{split}
+% \end{align}
+%where $\epsilon_t$ is the sentence number random effect and $\epsilon_{tm}$ is additional random noise. 
+Fitting the model to the observed classification performance of the different methods we are able to see if the probability of classifying correctly significantly vary between the methods.
+
+The statistical analysis is performed using the statistical program R \cite{R} and the R package \verb|lme4| \cite{lme4}.
+
+\subsection{Results}
+
 Table \ref{tab:2} shows the optimal parameter values of $d_p, d_n, t_p$ and $t_n$ tuned using the training set, and classification performance for the different methods on the test set using the parameter values tuned from the training set.
@@
   \centering
-  \begin{tabular}{lcccccl}
-       & $d_p$ & $d_n$ & $t_p$ & $t_n$ & Correct   & p-val \\ \hline
-    WD &    2  &   0  & 0.7  &  0.0  & 145 (47\%) & \\
-    A0 &    2  &   0  & 2.0  &  0.3  & 161 (52\%) & 0.023\\
-    CW &    2  &   0  & 2.0  &  0.3  & 161 (52\%) & 0.024\\
-    OD &    2  &   0  & 2.0  &  0.3  & 162 (53\%) & 0.016
+  \begin{tabular}{|l|cccccl|}
+\hline & $d_p$ & $d_n$ & $t_p$ & $t_n$ & \bf Accuracy   & \bf p-val \\ \hline
+    WD &    2  &   0  & 0.7  &  0.0  & 47\% & \\
+    A0 &    2  &   0  & 2.0  &  0.3  & 52\% & 0.023\\
+    CW &    2  &   0  & 2.0  &  0.3  & 52\% & 0.024\\
+    OD &    2  &   0  & 2.0  &  0.3  & 53\% & 0.016\\ \hline
   \end{tabular}
@@
 \end{table}
-We see that the sentiment shifter 'not' only has a positive effect on the classification performance when it is in front of the sentiment word.
+We see that $d_n = 0$, meaning that the sentiment shifter 'not' only has a positive effect on the classification performance when it is in front of the sentiment word.
 We see that using dependency distances (method A0) the classification results are significantly improved compared to using word distances in the sentence (method WD) (p-value = 0.023).
-Also classification based on important dependency paths (method OD) performs significantly better than WD.
+Also classification based on salient dependency paths (method OD) performs significantly better than WD.
 We also see that OD performs better than A0 (162 correct compared to 161), but this improvement is not statistically significant.
@@
 In this paper we have compared the use of word distance between target word and sentiment word against metrics incorporating syntactic information.
-Our results show that using dependency tree distances or important dependency paths, improves the classification performance compared to using word distance.
+Our results show that using dependency tree distances or salient dependency paths, improves the classification performance compared to using word distance.
 
-Manually selecting important dependency paths for the aim of sentiment analysis is a hard task.
+Manually selecting salient dependency paths for the aim of sentiment analysis is a hard task.
 A natural further step of our analysis is to expand the training and test material and use machine learning to see if there exists dependency paths that improve results compared to using dependency distance.

### 2014-03-21 manuscript.tex
PES last changes.

@@
    Spr\aa kbanken \\ The National Library \\ of Norway\\
-  {\tt Per.Solberg@nb.no}\\ \And
+  {\tt p.e.solberg@ifikk.uio.no}\\ \And
   Lilja \O vrelid \\
@@
 distributed between Norwegian Bokm{\aa}l and Nynorsk, the two Norwegian
-written standards. Only the Bokm{\aa}l subcorpus has been used here. A
-large proportion of the NDT is newspaper text, there are also
-parliament transcripts, government reports and texts with a more
-colloquial style from blogs. Detailed annotation guidelines in English
+written standards. Only the Bokm{\aa}l subcorpus has been used here. Detailed annotation guidelines in English
 will be made available in April 2014 \cite{Kinn2013}.

### 2014-03-21 manuscript.tex
Commented out names, other minor changes

@@
 
-\author{Hugo Lewi Hammer \\
-  Oslo and Akershus \\ University College \\ Department of Computer Science \\
-  {\tt hugo.hammer@hioa.no} \\ \And
-  Per Erik Solberg \\
-   Spr\aa kbanken \\ The National Library \\ of Norway\\
-  {\tt p.e.solberg@ifikk.uio.no}\\ \And
-  Lilja \O vrelid \\
-   Department of Informatics \\ University of Oslo\\
-  {\tt liljao@ifi.uio.no}}
+\author{First Author \\
+  Affiliation / Address line 1 \\
+  Affiliation / Address line 2 \\
+  Affiliation / Address line 3 \\
+  {\tt email@domain} \\\And
+  Second Author \\
+  Affiliation / Address line 1 \\
+  Affiliation / Address line 2 \\
+  Affiliation / Address line 3 \\
+  {\tt email@domain} \\}
+
+%% \author{Hugo Lewi Hammer \\
+%%   Oslo and Akershus \\ University College \\ Department of Computer Science \\
+%%   {\tt hugo.hammer@hioa.no} \\ \And
+%%   Per Erik Solberg \\
+%%    Spr\aa kbanken \\ The National Library \\ of Norway\\
+%%   {\tt p.e.solberg@ifikk.uio.no}\\ \And
+%%   Lilja \O vrelid \\
+%%    Department of Informatics \\ University of Oslo\\
+%%   {\tt liljao@ifi.uio.no}}
 
@@
 The first approach is based on applying the number of words between the target and the sentiment words to weight the sentence sentiment score.
-The second approach is based on using the shortest paths between target and sentiment words in a dependency graph and linguistically motivated syntactic patterns expressed as dependence paths.
-The methods is tested on a corpus of sentences from online Norwegian political discussions.
-The results show that the method based on dependency graph performs significantly better than the first approach.
+The second approach is based on using the shortest paths between target and sentiment words in a dependency graph and linguistically motivated syntactic patterns expressed as dependency paths.
+The methods are tested on a corpus of sentences from online Norwegian political discussions.
+The results show that the method based on dependency graphs performs significantly better than the word-based approach.
 \end{abstract}
@@
 the Obama 2012 election team initiated an extensive use of text analytics and machine learning techniques towards online material to guide advertising campaigns, identifying key voters, and improve fundraising \cite{Issenberg12}.
-There also has been a lot of concert about the alarming growth in hate and racism against minorities like Muslims, Jews and Gypsies in online discussions \cite{r6,s2}.
+There has also been a lot of concern about the alarming growth in hate and racism against minorities like Muslims, Jews and Gypsies in online discussions \cite{r6,s2}.
 Sentiment analysis (SA) is the discipline of automatically determining sentiment in text material and may be one important tool in understanding the diversity of opinions on the Internet.
@@
 Further let $sw_{j}, j \in \{1,2,\ldots,J\}$ be appearance number $j$ of a sentiment word in the sentence.
-Finally let $\textbf{ss} = (ss_1, ss_2, \ldots, ss_K)$ repressent the sentiment shifters in the sentence.
+Finally let $\textbf{ss} = (ss_1, ss_2, \ldots, ss_K)$ represent the sentiment shifters in the sentence.
 We compute a sentiment score, $S$, for the sentence as follows
@@
 Let $\mathcal{D}$ denote the set of all salient dependency paths.
-The function $\mathbf{gram}(tw_i, sw_{j})$ returns the dependency path, and if $\mathbf{gram}(tw_i, sw_{j}) \in \mathcal{D}$, then the function $W_{\mathbf{dep}}(tw_i, sw_{j}) \in [0,1]$, returns the importance of the path.
+The function $\mathbf{gram}(tw_i, sw_{j})$ returns the dependency path, and if $\mathbf{gram}(tw_i, sw_{j}) \in \mathcal{D}$, then the function $W_{\mathbf{dep}}(tw_i, sw_{j}) \in [0,1]$, returns the salience score of the path.
 Further let $\mathbf{depdist}(tw_i, sw_{j})$ return the dependency distance, as described above.
@@
 The debate articles were related to religion and immigration and we wanted to classify the sentiment towards all forms of the following target words: \textit{islam, muslim, quran, allah, muhammed, imam and mosque}.
-These are topics that typically create a lot of active discussions and disagreements.
+These represent topics that typically create a lot of active discussions and disagreements.
 

### 2014-04-23 manuscript.tex
Added old version of dependence path section

@@
 Sentiment analysis (SA) is the discipline of automatically determining sentiment in text material and may be one important tool in understanding the diversity of opinions on the Internet.
-SA has mostly been used to analyze opinions in comments and reviews about commercial products, but there are also examples of SA towards political tweets and discussions, see e.g.
-Tumasjan et al.
-\shortcite{Tumasjan2010}; Chen et al.
-\shortcite{Chen10}.
-SA of political discussions is known to be a difficult task since citations, irony and sarcasm is very common \cite{Bing12}.
 
@@
 
+\section{Previous work}
+
+Sentiment classification aims to classify a document or sentence as either positive or negative and sometimes also neutral.
+There are mainly two approaches, one based on machine learning and one based on based on using a list of words with given sentiment scores (lexicon-based approach).
+For machine learning any existing method can be used, e.g.
+na\"{\i}ve Bayes and support vector machine, \cite{Joachims99,Shawe00}.
+One simple lexicon-based approach is to count the number of words with positive and negative sentiment in the document as suggested by Hu and Liu \shortcite{Hu04}.
+One may classify the opinion of larger documents like movie or product reviews or smaller documents like tweets, comments or sentences.
+See Liu \shortcite{Bing12}, chapters three to five and references therein for the description of several opinion classification methods.
+
+SA has mostly been used to analyze opinions in comments and reviews about commercial products, but there are also examples of SA towards political tweets and discussions, see e.g.
+Tumasjan et al.
+\shortcite{Tumasjan2010}; Chen et al.
+\shortcite{Chen10}.
+SA of political discussions is known to be a difficult task since citations, irony and sarcasm is very common \cite{Bing12}.
+
 \section{Proposed SA methods}
@@
 Let $tw_i, i \in \{1,2,\ldots,I\}$ represent appearance number $i$ of the target word in the sentence.
+Note that we only consider one target word at the time.
+E.g.
+if a sentence contains two target words, e.g.
+Quran and Islam, the sentence is first classified with respect to Quran and then with respect to Islam.
 Further let $sw_{j}, j \in \{1,2,\ldots,J\}$ be appearance number $j$ of a sentiment word in the sentence.
@@
 \end{table}
+
+---------------------------------------------------
+
+A second way of determining the importance of a sentiment word towards a target based on syntactically parsed texts, is to establish a list of grammatical dependency paths between words, and test whether such paths exist between the target and the sentiment words in the material under investigation \cite{Jiang11}.
+The assumption would be that, if there is a meaningful grammatical relation between a target and a sentiment word, it is likely that they are semantically related to each other.
+Furthermore, it is reasonable to expect than some paths are stronger indicators of the overall sentiment of the sentence than others.
+To test this method, we have made a list of 42 grammatical dependency paths and given them a score between 1-3.
+The higher the score is, the better indicator of sentiment the path is assumed to be.
+In the following paragraphs, we will present our reasoning behind the choice of paths and the weight we have given them.
+The paths are written as follows: postag-target:postag-sentiment word{\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn({\textunderscore}{\textunderscore}DEPREL{\textunderscore}up/dn etc.).
+\emph{Up} and \emph{dn} show whether you move up or down in the dependency tree.
+So the relation between a noun target and a verb sentiment word where the noun is the subject of the verb, is represented as subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up.
+The relation between a target noun and a sentiment noun where the former is the subject and the latter is the direct object of the same verb, is subst:subst{\textunderscore}{\textunderscore}SUBST{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn.
+
+	A first group consists of paths from subject targets to sentiment predicates.
+Such paths can e.g.
+go from a subject to a verbal predicate, subst:verb{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up, as in (\ref{verbpred}), or from a subject to an adjectival or nominal predicate in the context of a copular verb, as in (\ref{adpred}), subst:adj{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn or subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}SPRED{\textunderscore}dn.
+
+	\begin{examples}
+	\item\label{verbpred}
+	\gll Ja, n{\aa} \textbf{jubler(sent.w.)} vel \textbf{muslimene(target)}.
+	yes now exult probably muslims+the
+	\glt 'Yes, the muslims probably exult now.'
+	\glend
+
+	\item\label{adpred}
+	\gll [...] for meg er \textbf{Muhammed(target)} like \textbf{levende(sent.w.)} som min far [...].
+	{} for me is Muhammad as alive as my father {}
+	\glt 'To me, Muhammad is as much alive as my dad is.'
+	\glend
+
+	\end{examples}
+
+	We have chosen to give subject-predicate paths the highest possible score, 3.
+Firstly, the combination of a subject and a predicate will result in a proposition, a statement which is evaluated as true or false \cite{Heim98}.
+We expect that a proposition typically will represent the opinion of the speaker, although e.g.
+irony and certain kinds of embedding can shift the truth evaluation in some cases \cite{Hooper73}.
+Secondly, if the predicate represents an event brought about by an intentional agent, such as \emph{jubler}, 'exult', in (\ref{verbpred}), the subject will typically represent that agent.
+If the predicate has a positive or negative sentiment, we expect that this sentiment is directed towards this intentional agent.
+
+	A second group we have considered, contains paths from subject targets to sentiment words embedded within the predicate.
+Examples of such paths are those from the subject to the nominal direct object of a verb, as in (\ref{subjobj}), subst:subst{\textunderscore}{\textunderscore}SUBJ{\textunderscore}up{\textunderscore}{\textunderscore}DOBJ{\textunderscore}dn.
+Paths from subjects into different kinds of adverbials are also a part of this group.
+
+	\begin{examples}
+	\item\label{subjobj}
+	\gll [...] ekstreme \textbf{muslimer(target)} beg{\aa}r \textbf{voldshandlinger(sent.w.)} [...].
+	{} extreme muslims commit {violent acts} {}
+	\glt 'Extreme muslims commit violent acts.'
+	\glend
+	\end{examples}
+
+	We consider paths from subjects to objects good indicators of sentiment and therefore give them the highest score, 3.
+The reasoning is much the same as for subject predicate paths: The statement is a proposition and the subject will often be the agent of the event.
+Also, the object, being an obligatory argument of the verb, is presumably closely semantically connected to it.
+Paths from subjects to adverbials, on the other hand, get a lower score, 2.
+This is because our experience is that the parser performs less well on adverbials.
+Also, adverbials are not obligatory arguments, and we therefore expect more semantic variation than for objects.
+
+	The paths in our third group go from targets to sentiment words within the predicate.
+These include paths from nominal direct object target to verbal predicates, as in (\ref{objverb}), subst:verb{\textunderscore}{\textunderscore}DOBJ{\textunderscore}up, and from various kinds of adverbials to verbal predicates, among other things:
+
+	\begin{examples}
+	\item\label{objverb}
+	\gll En Norsk dommer skal kontant \textbf{avvise(sent.w.)} \textbf{Sharia(target)} [...].
+	a Norwegian judge shall strictly reject sharia {}
+	\glt 'A Norwegian judge must strictly reject sharia.'
+	\glend
+	\end{examples}
+
+	We assume that predicate-internal paths are less good indicators of sentiment than the above groups, as predicates need to combine with a subject to form a proposition.
+Also, arguments within the predicate usually do not represent the intentional agent of the event.
+Such paths will get the score 1.
+
+	Our fourth and final group of dependency paths contains paths internal to the nominal phrase, such as from target nouns to attributive adjectives, as in (\ref{adjatr}), subst:adj{\textunderscore}{\textunderscore}ATR{\textunderscore}dn, and from target complements of attributive prepositions to target nouns, as in (\ref{substatr}), subst:subst{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ATR{\textunderscore}up:
+
+	\begin{examples}
+	\item\label{adjatr}
+	\gll [...] \textbf{fundamentalistisk(sent.w.}) \textbf{islam(target)} [...]
+	{} fundamentalist Islam {}
+	\glt 'fundamentalist Islam'
+	\glend
+
+	\item\label{substatr}
+	\gll [...] \textbf{kampen(sent.w} mot \textbf{islam(target)} [...]
+	{} fight+the against Islam {}
+	\glt 'the fight against Islam'
+	\glend
+
+	\end{examples}
+
+	We suspect paths internal to the nominal phrase to be relatively good indicators of sentiment: A positively or negatively qualified noun will probably often represent the sentiment of the speaker.
+At the same time, a nominal phrase of this kind can be used in many different contexts where the holder of the sentiment is not the speaker, so we therefore expect such paths to be somewhat less good indicators than subject-predicate paths.
+We therefore assign them the score 2.
+
+	Some complex paths receive a lower score than those indicated here, to compensate for parser inaccuracies.
+
+---------------------------------------------------
 

### 2014-04-24 manuscript.tex
PE's changes to the final text

@@
 Paths in this group can get the maximum score, 1.
-The combination of a subject and a predicate will result in a proposition, and we expect propositions to represent the opinion of the speaker in many cases.
+%The combination of a subject and a predicate will result in a proposition, and we expect propositions to represent the opinion of the speaker in many cases.
 Also, the subject will often refer to the intentional agent of an event.
+If the predicate has a positive or negative sentiment, we expect that this sentiment is directed towards this intentional agent.
+The combination of a subject and a predicate will result in a proposition, a statement which is evaluated as true or false.
+We expect that a proposition typically will represent the opinion of the speaker, although e.g.
+irony and certain kinds of embedding can shift the truth evaluation in some cases.
+Secondly, if the predicate represents an event brought about by an intentional agent, the subject will typically represent that agent.
 If the predicate has a positive or negative sentiment, we expect that this sentiment is directed towards this intentional agent.
@@
 Paths from subjects into different kinds of adverbials are also a part of this group.
-We consider paths from subjects to objects to be good indicators of sentiment and assign them the highest score, 1, based on the same arguments as for subject-predicate paths.
+We consider paths from subjects to objects to be good indicators of sentiment and assign them the highest score, 1
+%, based on the same arguments as for subject-predicate paths.
+.
+The reasoning is much the same as for subject predicate paths: The statement is a proposition and the subject will often be the agent of the event.
+Also, the object and the verb are presumably closely semantically connected, as the former is an argument of the latter.
 Paths into adverbials get lower values, as adverbials often are less semantically connected to the predicate than objects.
